### 2022-03-17 manuscript.Rmd
pdf added

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra & [coauthors]"
date: "09/03/2022"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
library(rgl)
rgl::setupKnitr()
rgl::rgl.open(); rgl::rgl.close() # first window in doc. may not render properly
```

### Introduction

Visualising neuroimaging data is one of the primary ways in which we
evaluate data quality, interpret results and communicate findings. These
visualisations are commonly produced using graphic interface-based (GUI)
tools where individual images are opened and display settings are
manually changed until the desired output is reached. While the choice
to use GUI-based software's has been driven by a perception of
convenience, flexibility and accessibility, there are now many
code-based software packages which are well-documented and don't often
require high-level knowledge of the programming. These tools are
flexible and allow for generation of reproducible, high-quality and
publication ready brain visualisations in only a few lines of code
(Figure 1), especially within the R, Python and Matlab environments.

This article will cover three major advantages of using code-generated
visualisations over GUI based tools: replicability, flexibility and
integration. First, by generating figures using code, you increase the
replicability of your figures for yourself, your collaborators and your
readers. Second, code-based software provide more precise controls over
visualisation settings, while also benefiting from advantages of
programming, such as being able to iteratively generate multiple
figures. Finally, being able to integrate figure generation into your
analysis scripts reduces changes of errors, with more advanced tools now
allowing for seamless weaving together of prose and code. Here, we
review the advantages of learning and using programmatic neuroimaging
visualisations, focusing on benefits to replicability, flexibility and
interactivity. We conclude by introducing examples of R-packages which
allow for visualisation of region-of-interest (ROI), voxel, vertex and
edge level data, followed by a brief discussion of limitations and
functionality gaps in code-based brain visualisation tools.

### Replicability

In recent years, there have been multiple large-scale efforts
empirically demonstrating the lack of reproducibility of findings from
neuroimaging data (cite). One common solution proposed for achieving
robust and reliable discoveries has been to encourage scientific output
which can be transparently evaluated and potentially replicated. In
practise, what this usually means is openly sharing detailed methods,
materials, code and data. While there is a trend towards increasing
transparency and code sharing in neuroimaging research (cite), the
sharing of code used to generate figures which include brain renderings
and spatial maps has been relatively neglected. This gap in
reproducibility is partly driven by the fact that brain figures are
often created using a manual process of tinkering with sliders, buttons
and overlays on a GUI, concluding with a screenshot and sometimes
beatification in image processing software like Illustrator. This
process inherently makes neuroimaging visualisations difficult, if not
impossible to replicate, even by the authors who created them.

Given that brain figures regularly form the centrepiece of
interpretation within a paper, conference presentations and news
reports, making sure they can be reliably regenerated is crucial for
knowledge generation. By writing and sharing code used to generate brain
visualisations, a direct and traceable link is established between the
underlying data and scientific figure. While the code that produces a
replicable figure doesn't reflect the validity of the scientific finding
or the accuracy of the content figure, it instils transparency and
robustness while demonstrating a desire to further scientific knowledge.
Some would even consider publishing figures which cannot be replicated
as closer to advertising, rather than science (cite blog).

### Flexibility

Being able to exactly replicate your figures via code has serious
advantages beyond good open science practises. In particular, the
ability to reprogram inputs (such as statistical maps) and settings
(such as colour schemes and visual orientations) can streamline your
entire scientific workflow. Being able to code the inputs and settings
allows for the easy production of multiple figures, such as those
resulting from multiple analyses which require similar visualisations.
Likewise, an arduous request from a reviewer to alter the data
processing or analysis becomes less of a burden when the figure can be
re-generated with a few lines of code, as opposed to re-pasting and
re-illustrating them. Having a code-base with reprogrammable inputs can
mean that the generation of visualisations requires less time, energy
and effort than manual GUI-based generation. Keep in mind that the gains
of writing code for your figures are cumulative, and in addition to
improving your programming, you start to build a codebase for figure
generation that you can continue to reuse and share through your
scientific career.

While brain visualisations are often thought of as the end results of
analyses, they also form a vital part of quality control of imaging
data. While tools to automatically detect artefacts, denoise the data
and generate derivatives are becoming more robust, we are not yet at the
stage where visualising the data during processing is no longer need.
Nonetheless, when working with large datasets such as Human Connectome
Project (cite) or UK BioBank (cite), it is infeasible to use traditional
GUI based tool to visually check the data. Knowing how to
programmatically generate brain visualisations can allow you to iterate
your code over each image of a large datasets making quality controls of
each data processing or analysis step accessible and achievable.

### Integrative and Interactive reporting

Often programming languages such as R, Python and Matlab are used for
the analysis in neuroimaging studuies, but the brain visualisation
resulting from these analyses is outsourced to a septate GIU-based
visualisation tools such as FSLeyes, Freeview or ITK-snap. Switching
from analysis to a GUI-based visualisation process be a cumbersome
deviation from the scientific workflow and can make debugging errors
more difficult, as you have to regularly switch program to visually
examine the results of any modifications to analyses. Using the brain
visulitsation ools that already exist within your chosen programming
environment can provide instant visual feedback on the impact of
modifications to processing or analyses. While some GUI-based tools do
offer command-line access to generate visualisations, they can lack
flexibility to easily generate publication ready figures and can lose
the benefits provided by your preferred programming environment.

Increasingly popular tools such as R-Markdown, Quarto and Jupyter
notebooks allow for the mixing of prose and code in a single script,
resulting in fully reproducible and publication ready papers. By using
code-based tools available within your preferred environment, brain
visualisations can be directly integrated and embedded within a paper or
report. Journals that publish neuroimaging studies are increasingly
moving towards allowing reproducible manuscripts, including reproducible
figures (cite e-life,f1000,plos), with with some even allowing on-demand
re-running of code using cloud services (cite).

Neuroimaging data are often spatially 3D and can have multiple time
points, adding a 4th dimensional (e.g. fMRI data). Thus, communicating
findings or evaluating quality using using static 2D slices is
challenging. While well-curated 3D renderings can help with spatial
localisation (cite madan), in the end, static images can only provide an
incomplete representation of the data. A added advantage of some of
code-based tools is that you can generate 'rich' media like interactive
figures or animations, which can improve scientific communication of
findings. Many code-based software tools now allow for the generation of
animated brain visualisations (cite blog) or interactive widgets which
allow users to zoom, rotate and scroll through slices. Linking to or
even embedding these videos or interactive figures in papers can greatly
enhance the communication of findings.

### Examples of neuroimaging visualisation packages available in R

##### *Voxel-level visualisations.*

The `oro.nifti` package allows for the reading, writing, manipulation
and visualisation of voxel-level imaging data of either *nifti*,
*analyze* or *afni* formats. In particular, the `image`, `slice` and
`orthographic` functions allow users to display the desired number of
slices in the desired orientations, while also providing precise control
over overlaied images, colour scales, legend placement and other
aesthetic settings (Fig 1A). Smoothing and re-sampling of images is
sometimes required for visualisation purposes, which can be achieved via
the *`ANTsR`* /`extrantsr` or `fslr` packages.

##### *Vertex-level visualisations.*

The recently developed `fsbrain` package allows for the visualisation of
vertex-level and atlas-level data obtained using Freesurfer. It contains
many flexible functions for visualising individual-level and group-level
measures such as cortical thickness, volume or surface area (Fig 1B).
The package also comes with extensive guides and documentations to
assist users (cite).

CIFTI or 'grey-ordinate' data is becoming a popular format for
structural and functional imaging data, as it combines vertex-level data
of the cortex with voxel-level data fo the cerebellum and sub-cortex. In
R, CIFTI data can now be read, visualised and manipulated using the
well-documented `ciftiTools` package (Fig 1C; cite).

##### *ROI-level visualisations.*

Statistical parameters can be mapped onto discreet cortical and
subcortical regions using the `ggseg` and `ggseg3d` package. These
packages flexibly generates aesthetic renderings of cortical,
subcortical and white matter ROIs in 2D and 3D (Fig 1D). Usually,
ROI-level interpretations are dependent on a standerdised atlas or
parcellation schemes the brain, accordingly this package and its add-ons
(`ggExtra`) provides a large array of commonly used atlases and some
functionality for users to contribute other atlases. Additionally, being
part of the 'Grammar of Graphics' frame work allows for integration with
packages such as `gganimate`, enabling users to animate and visualise
dynamic changes in spatial and temporal statistics across ROIs. The
`ciftiTools` package also allows for surface and voxel-level
visualisation of ROIs for the cortex and subcortex respectively (Fig
1E). Flexibly allowing CIFTI format atlases and ROIs to be displayed.

##### Edge-level visualisations.

Analyses which divide the brain into discrete regions and examine
pair-wise dependences between regional phenotypes are becoming
increasingly common. Often the results of these dependency analyses are
statistics relating to 'edges' or links between any two regions. The
package `brainconn` allows users to plot brain regions as nodes of a
network graph, and dependences between regions as edges of that graph,
in both 2D and interactive 3D (Figure 1D). Similar to `ggseg`, this
package comes within multiple commonly used atlases and contains
functionality for users to enter their own atlas schemes.

### Limitations and functionality gaps in R packages for brain visualisation

-   While most of these tools do not require a strond knowledge of
    programming, there can still be a steeper learning curve when
    compared to GUI-based tools.

-   For quick and interactive viewing of single images, sometimes GUI
    tools can be faster (although, fsleyes can be called from python and
    R environments with ease)

-   Visualising data-types such as streamlines from DWI-based
    tractography are still not well represented in code-based tools.

    -   But fsbrain has a function;
        <https://github.com/dfsp-spirit/fsbrain/blob/cb1b9d667a9449b214b20f6420038af2541e48b4/R/vis_dti_tracks.R>)

-   For tools which require non-standard or uncommon atlases or ROIs.

    -   Although, with `ciftitools`, this becomes easier, as long as
        atlas follows the CIFTI convention.

-   3D renderings of non-standard ROIs like unique subcortical schemes
    or brain stem are still difficult to do.

    -   Have to use complex tools like pyVista

### Figure 1

-   The below figures will be combined into a multi-panel figure with
    the corresponding code underneath.

```{r}
#Figure 1A
#voxel 1

# ADD COMMENTS TO EXPLAIN EACH LINE

library(neurobase)

template <- readnii('data/MNI152_T1_1mm_brain.nii.gz') #load the nifti file into R

effect <- readnii("data/MNI152_effect_size.nii.gz")

#threshold the effect at the desired cut-off
effect[effect<0.3] <- NA

#Plot the effect on the brain template
ortho2(x = template, 
       y = effect, 
       crosshairs = F, 
       bg = "white", 
       NA.x = T, 
       col.y  = hotmetal(), 
       xyz = c(70,50,80),
       useRaster = T,
       ybreaks = seq(0.3, 1, length.out = 65), 
       ycolorbar = TRUE, 
       mfrow = c(1,3))

```

```{r}
#Figure 1B
#voxel 2

library(neurobase)

library(scales)

dti <- readnii('data/sub-001__t1_warped.nii.gz') #load the nifti file into R

atlas <-  readnii('data/sub-001_schaefer300n7_aseg_to_dwispace_gm_rois.nii.gz')

overlay(x=robust_window(dti), y=atlas, 
               plot.type = "single", 
               z=c(seq(25,110,5)), 
               col.y =  alpha(rainbow(300), 0.3),
               plane = "axial",  
               useRaster = T, 
               bg = "white",NA.x=T, 
               zlim.y =c(1,300))

```

```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE}
#vertex 1
#Figure 1B

library(rgl)

# Load the package and point to the Connectome Workbench
suppressPackageStartupMessages(library(ciftiTools))

ciftiTools.setOption("wb_path", "/Applications/workbench/")

# Read and visualize a CIFTI file

cifti_fname <- ciftiTools::ciftiTools.files()$cifti["dtseries"]
surfL_fname <- ciftiTools.files()$surf["left"]

cii <- read_cifti(
  cifti_fname, brainstructures="left", 
  surfL_fname=surfL_fname)

view_xifti_surface(cii, 
                   hemisphere = "left", 
                   view = "lateral", 
                   idx = 1,
                   colors = viridis::viridis(n = 100),
                   zlim = c(1,1.5), legend_embed = T)

```

```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE}
#Vertex 2
#Figure 1X - Remove white space

library("fsbrain")

subjects_dir = fsbrain::get_optional_data_filepath("subjects_dir")

subject_id = 'subject1'

colourmap = colorRampPalette(viridis::viridis(n = 100))

vis.subject.morph.native(subjects_dir = subjects_dir, 
                         subject_id = 'subject1', 
                         measure = 'thickness', 
                         hemi='both', 
                         views="t4",
                         draw_colorbar = "horizontal",
                         cortex_only = T, surface = "white",
                         makecmap_options = list('colFn'=colourmap))

```

```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE, fig.show='hold'}
#ROI1 
#Figure 1X - Remove white space

parc <- load_parc("Yeo_7")
plot1 <- view_xifti_surface(parc,  
                           legend_embed = T,
                           hemisphere = "right")
```

```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE, fig.show='hold'}
#ROI1 
#Figure 1X - combine with previous figure

set.seed(1993) #set a random seed (good practice for reproducibility)

parc <- load_parc("Schaefer_400")
ramdom_metric <- rnorm(400)
cii <- move_from_mwall(cii, NA)

parc_vec <- c(as.matrix(parc))
xii_metric <- c(NA, ramdom_metric)[parc_vec + 1]

xii1 <- select_xifti(cii, 1)
xii_metric <- newdata_xifti(xii1, xii_metric)

plot2 <- view_xifti_surface(xii_metric, 
     colors = viridis::viridis(n = 400), 
     borders = "black", 
     hemisphere = "left", )

```

```{r}
#ROI2

#devtools::install_github("LCBC-UiO/ggsegGlasser")
library(ggseg)
library(ggplot2)
library(ggsegGlasser)

set.seed(1993) #set a random seed (good practice for reproducibility)

base_atlas <- as.data.frame(na.omit(cbind(glasser$data$region, glasser$data$hemi)))

colnames(base_atlas) <- c("region", "hemi")

Effect <- rnorm(dim(base_atlas)[1]) #generate a random numbers for each roi in the atlas

base_atlas <- cbind(Effect, base_atlas)

cortex <- ggseg(atlas = glasser,
      .data = base_atlas,
      mapping=aes(fill=Effect), 
      position="stacked",
      colour="black",
      size=.2,
      show.legend = F) + scale_fill_viridis_b()

sub_base_atlas <- as.data.frame(na.omit(cbind(aseg$data$region, aseg$data$hemi)))

colnames(sub_base_atlas) <- c("region", "hemi")

Effect <- rnorm(dim(sub_base_atlas)[1])

sub_base_atlas <- cbind(Effect, sub_base_atlas)

subcortex <- ggseg(atlas = aseg,
      .data = sub_base_atlas,
      hemisphere = "right",
      mapping=aes(fill=Effect), 
      position="stacked",
      colour="black",
      size=.2,
      show.legend = T) + 
  scale_fill_viridis_b()

cowplot::plot_grid(cortex, subcortex, nrow = 1, rel_widths = c(1,.7))

```
```{r}
#Edge (also add 3d version)
#Fig1X

#remotes::install_github("sidchop/brainconn")
library(brainconn)

conmat <- example_weighted_undirected
degree <- rowSums(conmat)[which(rowSums(conmat)!=0)]
brainconn(atlas ="schaefer300_n7", 
          conmat=conmat, 
          node.size = degree/2,
          view="ortho", 
          edge.color.weighted = T,
          background.alpha = 0.4, 
          show.legend = F,
          edge.color = scale_edge_colour_gradient2(low='yellow', mid='orange', high='red'))

```

### 2022-03-17 manuscript.Rmd
.html/.docx added

@@
 output:
+  html_document: default
+  word_document: default
   pdf_document: default
-  html_document: default
 editor_options:

### 2022-03-18 manuscript.Rmd
sp check

--- 2022-03-17 manuscript.Rmd
@@
 output:
+  word_document: default
   pdf_document: default
@@
 code-based software packages which are well-documented and don't often
-require high-level knowledge of the programming. These tools are
+require high-level knowledge of programming. These tools are
 flexible and allow for generation of reproducible, high-quality and
@@
 Often programming languages such as R, Python and Matlab are used for
-the analysis in neuroimaging studuies, but the brain visualisation
+the analysis in neuroimaging studies, but the brain visualisation
 resulting from these analyses is outsourced to a septate GIU-based
@@
 examine the results of any modifications to analyses. Using the brain
-visulitsation ools that already exist within your chosen programming
+visualisation tools that already exist within your chosen programming
 environment can provide instant visual feedback on the impact of
@@
 points, adding a 4th dimensional (e.g. fMRI data). Thus, communicating
-findings or evaluating quality using using static 2D slices is
+findings or evaluating quality using static 2D slices is
 challenging. While well-curated 3D renderings can help with spatial

### 2022-03-18 manuscript.Rmd
sp check

@@
 figures. Finally, being able to integrate figure generation into your
-analysis scripts reduces changes of errors, with more advanced tools now
+analysis scripts reduces chances of errors, with more advanced tools now
 allowing for seamless weaving together of prose and code. Here, we

### 2022-03-31 manuscript.Rmd
figure compiled

@@
 title: "Reproducible and programmatic generation of neuroimaging visualisations"
-author: "Sidhant Chopra & [coauthors]"
+author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
 date: "09/03/2022"
 output:
+  pdf_document: default
   word_document: default
-  pdf_document: default
   html_document: default
@@
 code-based software packages which are well-documented and don't often
-require high-level knowledge of programming. These tools are
-flexible and allow for generation of reproducible, high-quality and
-publication ready brain visualisations in only a few lines of code
-(Figure 1), especially within the R, Python and Matlab environments.
+require high-level knowledge of programming. These tools are flexible
+and allow for generation of reproducible, high-quality and publication
+ready brain visualisations in only a few lines of code (Figure 1),
+especially within the R, Python and Matlab environments.
 
@@
 points, adding a 4th dimensional (e.g. fMRI data). Thus, communicating
-findings or evaluating quality using static 2D slices is
-challenging. While well-curated 3D renderings can help with spatial
-localisation (cite madan), in the end, static images can only provide an
-incomplete representation of the data. A added advantage of some of
-code-based tools is that you can generate 'rich' media like interactive
-figures or animations, which can improve scientific communication of
-findings. Many code-based software tools now allow for the generation of
-animated brain visualisations (cite blog) or interactive widgets which
-allow users to zoom, rotate and scroll through slices. Linking to or
-even embedding these videos or interactive figures in papers can greatly
-enhance the communication of findings.
+findings or evaluating quality using static 2D slices is challenging.
+While well-curated 3D renderings can help with spatial localisation
+(cite madan), in the end, static images can only provide an incomplete
+representation of the data. A added advantage of some of code-based
+tools is that you can generate 'rich' media like interactive figures or
+animations, which can improve scientific communication of findings. Many
+code-based software tools now allow for the generation of animated brain
+visualisations (cite blog) or interactive widgets which allow users to
+zoom, rotate and scroll through slices. Linking to or even embedding
+these videos or interactive figures in papers can greatly enhance the
+communication of findings.
 
@@
 slices in the desired orientations, while also providing precise control
-over overlaied images, colour scales, legend placement and other
+over overlaid images, colour scales, legend placement and other
 aesthetic settings (Fig 1A). Smoothing and re-sampling of images is
@@
 the *`ANTsR`* /`extrantsr` or `fslr` packages.
+
+[view_xifti_volume(xii, interactive = TRUE) in cifti tools]
 
@@
 Statistical parameters can be mapped onto discreet cortical and
-subcortical regions using the `ggseg` and `ggseg3d` package. These
+sub-cortical regions using the `ggseg` and `ggseg3d` package. These
 packages flexibly generates aesthetic renderings of cortical,
-subcortical and white matter ROIs in 2D and 3D (Fig 1D). Usually,
-ROI-level interpretations are dependent on a standerdised atlas or
+sub-cortical and white matter ROIs in 2D and 3D (Fig 1D). Usually,
+ROI-level interpretations are dependent on a standardised atlas or
 parcellation schemes the brain, accordingly this package and its add-ons
@@
 `ciftiTools` package also allows for surface and voxel-level
-visualisation of ROIs for the cortex and subcortex respectively (Fig
+visualisation of ROIs for the cortex and sub-cortex respectively (Fig
 1E). Flexibly allowing CIFTI format atlases and ROIs to be displayed.
@@
 
--   The below figures will be combined into a multi-panel figure with
-    the corresponding code underneath.
+```{r Figure1 }
+library(patchwork)
+library(ggplot2)
 
-```{r}
+fig1a <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1a.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1b <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1b.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1c <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1c.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1d <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1d.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1e <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1e.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1f <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1f.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1g1 <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1g1.png"),
+                                                        width=ggplot2::unit(1,"npc"),
+                                                        height=ggplot2::unit(1,"npc")))
+fig1g2 <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1g2.png"),
+                                                        width=ggplot2::unit(1,"npc"),
+                                                        height=ggplot2::unit(1,"npc")))
+
+fig1h <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1h.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+fig1i <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1i.png"),
+                                                       width=ggplot2::unit(1,"npc"),
+                                                       height=ggplot2::unit(1,"npc")))
+
+patchwork <- fig1a/fig1b|(fig1c|fig1f)/fig1d|(fig1e|fig1g2)/fig1g1|fig1h/fig1i
+
+patchwork + plot_annotation(tag_levels = 'A',
+                            title = 'Examples of brain visualisations in R')
+
+```
+
+```{r Fig1a, eval=FALSE}
 #Figure 1A
@@
 library(neurobase)
+library(ggplotify)
 
@@
 #Plot the effect on the brain template
+breaks = seq(.3,.6, by=0.005)
+
+png("data/fig1a.png") 
 ortho2(x = template, 
@@
        NA.x = T, 
-       col.y  = hotmetal(), 
+       col.y= hotmetal(), 
        xyz = c(70,50,80),
        useRaster = T,
-       ybreaks = seq(0.3, 1, length.out = 65), 
        ycolorbar = TRUE, 
-       mfrow = c(1,3))
+       mfrow = c(1,3)) +
+  colorbar(breaks,col = hotmetal(n=length(breaks)-1), 
+           text.col = "black", labels = TRUE, maxleft = 0.95) + 
+  title(main = "Voxel Statistic Map")
+dev.off()
 
@@
 
-```{r}
+```{r Fig1b, eval=FALSE }
 #Figure 1B
@@
 library(neurobase)
-
 library(scales)
@@
 
+png('data/fig1b.png')
 overlay(x=robust_window(dti), y=atlas, 
         plot.type = "single", 
-               z=c(seq(25,110,5)), 
+        z=c(seq(30,110,10)), 
         col.y =  alpha(rainbow(300), 0.3),
@@
         useRaster = T, 
-               bg = "white",NA.x=T, 
-               zlim.y =c(1,300))
+        bg = "white",
+        NA.x=T, 
+        zlim.y =c(1,300), 
+        mar = c(0.1, 0.1, 1.5, 0.1)) + #marget of bottom, left, top, right borders
+  title("Voxel Atlas Overlay", line = 1.3)
+dev.off()
 
@@
 
-```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE}
+```{r Fig1c , eval=FALSE}
 #vertex 1
 #Figure 1B
-
 library(rgl)
-
+library(ggplot2)
 # Load the package and point to the Connectome Workbench
@@
                    hemisphere = "left", 
-                   view = "lateral", 
+                   view = "both", 
                    idx = 1,
                    colors = viridis::viridis(n = 100),
-                   zlim = c(1,1.5), legend_embed = T)
+                   zlim = c(1,1.5),  
+                   legend_embed = T,
+                   title = "Vertex Statistic Map", 
+                   cex.title = 2)
+
+rgl.snapshot("data/fig1c.png")
+rgl.close()
 
@@
 
-```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE}
+```{r Fig1d , eval=FALSE}
 #Vertex 2
@@
 
-library("fsbrain")
+library(fsbrain)
 
-subjects_dir = fsbrain::get_optional_data_filepath("subjects_dir")
+#download_optional_data()
+subjects_dir = get_optional_data_filepath("subjects_dir")
 
@@
                          hemi='both', 
-                         views="t4",
+                         views = 't4',
                          draw_colorbar = "horizontal",
@@
                          makecmap_options = list('colFn'=colourmap))
+rgl.snapshot("data/fig1d.png")
+rgl.close()
 
@@
 
-```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE, fig.show='hold'}
+```{r Fig1e , eval=FALSE}
 #ROI1 
-#Figure 1X - Remove white space
-
+#Figure 1e 
+suppressPackageStartupMessages(library(ciftiTools))
 parc <- load_parc("Yeo_7")
-plot1 <- view_xifti_surface(parc,  
+view_xifti_surface(parc,  
                    legend_embed = T,
                    hemisphere = "right")
+
+rgl.snapshot("data/fig1e.png")
+
+rgl.close()
+
 ```
 
-```{r, fig.cap="Snapshot", rgl=TRUE, format="png", eval=TRUE, fig.show='hold'}
+```{r Fig1f , eval=FALSE}
 #ROI1 
@@
 parc <- load_parc("Schaefer_400")
+
 ramdom_metric <- rnorm(400)
+
 cii <- move_from_mwall(cii, NA)
@@
 parc_vec <- c(as.matrix(parc))
+
 xii_metric <- c(NA, ramdom_metric)[parc_vec + 1]
@@
 xii1 <- select_xifti(cii, 1)
+
 xii_metric <- newdata_xifti(xii1, xii_metric)
@@
 
+rgl.snapshot("data/fig1f.png")
+
+rgl.close()
+
 ```
 
-```{r}
+```{r Fig1g, eval=FALSE}
 #ROI2
@@
                 size=.2,
-      show.legend = F) + scale_fill_viridis_b()
+                show.legend = F,
+                plot.background = "white") + scale_fill_viridis_b()
 
@@
                    size=.2,
-      show.legend = T) + 
+                   show.legend = T, 
+                   plot.background = "white") + 
   scale_fill_viridis_b()
 
-cowplot::plot_grid(cortex, subcortex, nrow = 1, rel_widths = c(1,.7))
+#fig1g <- cowplot::plot_grid(cortex, subcortex, nrow = 1, rel_widths = c(1,.7))
+
+ggsave(filename = 'data/fig1g1.png', plot = cortex, device = 'png', bg = 'white')
+ggsave(filename = 'data/fig1g2.png', plot = subcortex, device = 'png', bg = 'white')
 
 ```
-```{r}
+
+```{r Fig1h , eval = F}
 #Edge (also add 3d version)
@@
 degree <- rowSums(conmat)[which(rowSums(conmat)!=0)]
-brainconn(atlas ="schaefer300_n7", 
+fig1h <- brainconn(atlas ="schaefer300_n7", 
                    conmat=conmat, 
@@
                    edge.color = scale_edge_colour_gradient2(low='yellow', mid='orange', high='red')) 
+ggsave(filename = 'data/fig1h.png', plot = fig1h, device = 'png', bg = 'white')
+
+brainconn3D(atlas ="schaefer300_n7", 
+            conmat=conmat,
+            show.legend = F)
 

### 2022-04-01 manuscript.Rmd
manuscript update and fig compile

@@
 output:
+  html_document: default
+  word_document: default
   pdf_document: default
-  word_document: default
-  html_document: default
 editor_options:
@@
 knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
-library(rgl)
-rgl::setupKnitr()
-rgl::rgl.open(); rgl::rgl.close() # first window in doc. may not render properly
 ```
@@
 tools where individual images are opened and display settings are
-manually changed until the desired output is reached. While the choice
-to use GUI-based software's has been driven by a perception of
-convenience, flexibility and accessibility, there are now many
+manually changed until the desired output is reached. The choice to use
+GUI-based software's has been driven by a perception of convenience,
+flexibility and accessibility. However now there are also many
 code-based software packages which are well-documented and don't often
-require high-level knowledge of programming. These tools are flexible
-and allow for generation of reproducible, high-quality and publication
-ready brain visualisations in only a few lines of code (Figure 1),
-especially within the R, Python and Matlab environments.
+require high-level knowledge of programming, making them more accessible
+to the neuroimaging community. These tools are flexible and allow for
+the generation of reproducible, high-quality and publication-ready brain
+visualisations in only a few lines of code (Figure 1), especially within
+the R, Python and Matlab environments.
 
@@
 replicability of your figures for yourself, your collaborators and your
-readers. Second, code-based software provide more precise controls over
+readers. Second, code-based software provides more precise controls over
 visualisation settings, while also benefiting from advantages of
@@
 visualisations, focusing on benefits to replicability, flexibility and
-interactivity. We conclude by introducing examples of R-packages which
-allow for visualisation of region-of-interest (ROI), voxel, vertex and
-edge level data, followed by a brief discussion of limitations and
-functionality gaps in code-based brain visualisation tools.
+intergration. We conclude by introducing examples of R-packages which
+allow for visualisation of statistics at region-of-interest (ROI),
+voxel, vertex and edge level data, followed by a brief discussion of
+limitations and functionality gaps in code-based brain visualisation
+tools.
 
@@
 empirically demonstrating the lack of reproducibility of findings from
-neuroimaging data (cite). One common solution proposed for achieving
-robust and reliable discoveries has been to encourage scientific output
-which can be transparently evaluated and potentially replicated. In
-practise, what this usually means is openly sharing detailed methods,
-materials, code and data. While there is a trend towards increasing
-transparency and code sharing in neuroimaging research (cite), the
-sharing of code used to generate figures which include brain renderings
-and spatial maps has been relatively neglected. This gap in
-reproducibility is partly driven by the fact that brain figures are
-often created using a manual process of tinkering with sliders, buttons
-and overlays on a GUI, concluding with a screenshot and sometimes
-beatification in image processing software like Illustrator. This
-process inherently makes neuroimaging visualisations difficult, if not
-impossible to replicate, even by the authors who created them.
+neuroimaging data (cite poldrack). One common solution proposed for
+achieving robust and reliable discoveries has been to encourage
+scientific output which can be transparently evaluated and independently
+replicated. In practise, what this usually means is openly sharing
+detailed methods, materials, code and data. While there is a trend
+towards increasing transparency and code sharing in neuroimaging
+research (cite), the sharing of code used to generate figures which
+include brain renderings and spatial maps has been relatively neglected.
+This gap in reproducibility is partly driven by the fact that brain
+figures are often created using a manual process of tinkering with
+sliders, buttons and overlays on a GUI, concluding with a screenshot and
+sometimes beatification in image processing software like Illustrator.
+This process inherently makes neuroimaging visualisations difficult, if
+not impossible to replicate, even by the authors who created them.
 
@@
 (such as colour schemes and visual orientations) can streamline your
-entire scientific workflow. Being able to code the inputs and settings
-allows for the easy production of multiple figures, such as those
-resulting from multiple analyses which require similar visualisations.
-Likewise, an arduous request from a reviewer to alter the data
-processing or analysis becomes less of a burden when the figure can be
-re-generated with a few lines of code, as opposed to re-pasting and
-re-illustrating them. Having a code-base with reprogrammable inputs can
-mean that the generation of visualisations requires less time, energy
-and effort than manual GUI-based generation. Keep in mind that the gains
-of writing code for your figures are cumulative, and in addition to
-improving your programming, you start to build a codebase for figure
-generation that you can continue to reuse and share through your
-scientific career.
+entire scientific workflow. Changing inputs and settings via code allows
+for the easy production of multiple figures, such as those resulting
+from multiple analyses which require similar visualisations. While some
+GUI-based tools do offer command-line access to generate visualisations,
+they can lack flexibility to easily generate publication ready figures
+and can lose the benefits, such as iteration, provided by your preferred
+programming environment. A simple for-loop or copying and pasting the
+code with the input and/or setting-of-interest modified can be a
+powerful method for exploring visualisation options or creating
+multi-panel figures. Likewise, an arduous request from a reviewer to
+alter the data processing or analysis becomes less of a burden when the
+figure can be re-generated with a few lines of code, as opposed to
+re-pasting and re-illustrating them. Having a code-base with
+reprogrammable inputs can mean that the generation of visualisations
+requires less time, energy and effort than manual GUI-based generation.
+This also makes it easier to make figures for each subsequent project
+that you work on. Keep in mind that the gains of writing code for your
+figures are cumulative, and in addition to improving your programming,
+you start to build a code-base for figure generation that you can
+continue to reuse and share through your scientific career.
+
+Precise controls via code over visualization settings, such as colour
+schemes, legend placement and camera angles, can provide you with much
+greater flexibility over visualisations. Nonetheless, part of the appeal
+of GUI-based tools is that the pre-sets for such settings can provide a
+useful starting point and reduce the decision burden on the user.
+However, similar pre-sets are often available in the from of default
+settings in most code-based packages, negating the need for the user to
+manually enter each and every choice of setting required for making the
+image. Most code-based tools also come with detialed documentation, or
+even entire papers (cite ggseg and ciftitools) which provide examples of
+figures which can be used as starting points or templates for new users.
+As the popularity of code-sharing for figure increases, there will be an
+cornucopia of templates that can be used as starting points for new
+figures.
 
@@
 analyses, they also form a vital part of quality control of imaging
-data. While tools to automatically detect artefacts, denoise the data
-and generate derivatives are becoming more robust, we are not yet at the
+data. Tools to automatically detect artefacts, de-noise the data and
+generate derivatives are becoming more robust, but we are not yet at the
 stage where visualising the data during processing is no longer need.
 Nonetheless, when working with large datasets such as Human Connectome
-Project (cite) or UK BioBank (cite), it is infeasible to use traditional
-GUI based tool to visually check the data. Knowing how to
+Project (cite) or UK BioBank (cite), it is unfeasible to use traditional
+GUI-based tool to visually check the data. The time it takes to open a
+single file and achieve the desired visualisation settings vastly
+compounds when working with large datasets. Knowing how to
 programmatically generate brain visualisations can allow you to iterate
-your code over each image of a large datasets making quality controls of
-each data processing or analysis step accessible and achievable.
+your visualisation code over each image of a large datasets making
+checking the quality of each data processing or analysis step accessible
+and achievable. The visual outputs of each iteration can be complied
+into accessible documents which can be easily scrolled, with more
+advanced usage allowing for the creation of interactive HTML reports,
+similar to those created by tools like mriQC (cite). Increasing capacity
+to conduct visual quality control on larger datasets can increase the
+identification of processing errors and result in more reliable and
+valid findings from your data.
 
@@
 the analysis in neuroimaging studies, but the brain visualisation
-resulting from these analyses is outsourced to a septate GIU-based
+resulting from these analyses is outsourced to separate GIU-based
 visualisation tools such as FSLeyes, Freeview or ITK-snap. Switching
-from analysis to a GUI-based visualisation process be a cumbersome
-deviation from the scientific workflow and can make debugging errors
-more difficult, as you have to regularly switch program to visually
-examine the results of any modifications to analyses. Using the brain
-visualisation tools that already exist within your chosen programming
-environment can provide instant visual feedback on the impact of
-modifications to processing or analyses. While some GUI-based tools do
-offer command-line access to generate visualisations, they can lack
-flexibility to easily generate publication ready figures and can lose
-the benefits provided by your preferred programming environment.
+from your analysis environment to a GUI-based visualisation process be a
+cumbersome deviation from the scientific workflow. This can make
+debugging errors more difficult, as you have to regularly switch program
+to visually examine the results of any modifications to analyses. Using
+the brain visualisation tools that already exist within your chosen
+programming environment can provide instant visual feedback on the
+impact of modifications to processing or analyses.
 
 Increasingly popular tools such as R-Markdown, Quarto and Jupyter
-notebooks allow for the mixing of prose and code in a single script,
+Notebook allow for the mixing of prose and code in a single script,
 resulting in fully reproducible and publication ready papers. By using
@@
 visualisations can be directly integrated and embedded within a paper or
-report. Journals that publish neuroimaging studies are increasingly
-moving towards allowing reproducible manuscripts, including reproducible
-figures (cite e-life,f1000,plos), with with some even allowing on-demand
+report. Some journals that publish neuroimaging studies are moving
+towards allowing reproducible manuscripts, including reproducible
+figures (cite e-life,f1000,plos), with some even allowing on-demand
 re-running of code using cloud services (cite).
@@
 Neuroimaging data are often spatially 3D and can have multiple time
-points, adding a 4th dimensional (e.g. fMRI data). Thus, communicating
+points, adding a 4th dimension (e.g. fMRI data). Thus, communicating
 findings or evaluating quality using static 2D slices is challenging.
-While well-curated 3D renderings can help with spatial localisation
-(cite madan), in the end, static images can only provide an incomplete
-representation of the data. A added advantage of some of code-based
-tools is that you can generate 'rich' media like interactive figures or
-animations, which can improve scientific communication of findings. Many
-code-based software tools now allow for the generation of animated brain
-visualisations (cite blog) or interactive widgets which allow users to
-zoom, rotate and scroll through slices. Linking to or even embedding
-these videos or interactive figures in papers can greatly enhance the
-communication of findings.
+While well curated 3D renderings can help with spatial localisation
+(cite madan), in the end, static 2D images can only provide an
+incomplete representation of 3D or 4D data. A added advantage of some of
+code-based tools is that you can generate 'rich' media like interactive
+figures or animations, which can improve scientific communication of
+findings. Many code-based software tools now allow for the generation of
+animated brain visualisations (cite blog) or interactive widgets which
+allow users to zoom, rotate and scroll through slices. Linking to or
+even embedding these videos or interactive figures in papers can greatly
+enhance the communication of findings.
+
+Neuroimaging data are often spatially 3D and can have multiple time
+points, adding a 4th dimension (e.g. fMRI data). Thus, communicating
+findings or evaluating quality using static 2D slices is challenging,
+and may not be the best representation of the data, or the
+interpretations. While well-curated 3D renderings can help with spatial
+localisation (see madan), in the end, static images can only provide an
+incomplete representation of the data, and forces researchers to choose
+the best angle to show, which often involves compromising one result for
+another. An added advantage of some of the code-based tools is that you
+can generate 'rich' media like interactive widgets -- figures or
+animations, which allow users to zoom, rotate and scroll through slices.
+Interacting with a figure in this way can improve scientific
+communication of findings. Linking to or even embedding these videos or
+interactive figures in papers can greatly enhance the communication of
+findings and make your paper more engaging for the reader. Such rich
+brain visualisations lend themselves to being embedded or shared on
+science communication mediums other than academic papers - such as
+presentations, web-sites and social media - all of which can promote the
+communication of your research with peers and a reach larger audiences.
 
@@
 
-##### *Voxel-level visualisations.*
+The following four sections provide brief examples packages and
+functions available in R for visualising voxel, vertex, ROI and
+edge-level data. A more didactic introduction to these tools is provided
+in a [collection of beginner friendly
+R-Notebooks](https://github.com/sidchop/neuRo-vis-BrainHack-2021).
+
+### Figure 1
+
+```{r Figure1 , echo=FALSE}
+library(patchwork)
+library(ggplot2)
+
+#loop this?
+fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1h', 'fig1i')
+figs <- list()
+
+for (f in 1:length(fig_name)) { 
+  figs[[f]] <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/',fig_name[f],'.png')),
+                                                             width=ggplot2::unit(1,"npc"),
+                                                             height=ggplot2::unit(1,"npc")))
+}
+
+patchwork <- figs[[1]]/figs[[2]]|(figs[[3]]|figs[[6]])/figs[[4]]|(figs[[5]]|figs[[8]])/figs[[7]]|figs[[9]]/figs[[10]]
+
+#& theme(text = element_text('Times New Roman'))
+
+patchwork + plot_annotation(tag_levels = 'A',
+                            title = 'Examples of brain visualisations in R')
+
+```
+
+\
+*[Figure 1 - Add Caption]*
+
+##### Voxel-level visualisations.
 
 The `oro.nifti` package allows for the reading, writing, manipulation
-and visualisation of voxel-level imaging data of either *nifti*,
-*analyze* or *afni* formats. In particular, the `image`, `slice` and
-`orthographic` functions allow users to display the desired number of
-slices in the desired orientations, while also providing precise control
-over overlaid images, colour scales, legend placement and other
-aesthetic settings (Fig 1A). Smoothing and re-sampling of images is
-sometimes required for visualisation purposes, which can be achieved via
-the *`ANTsR`* /`extrantsr` or `fslr` packages.
+and visualisation of voxel-level imaging data of either nifti, analyze
+or afni formats. In particular, the `image`, `slice` and `orthographic`
+functions allow users to display the desired number of slices in the
+desired orientations, while also providing precise control over overlaid
+images, colour scales, legend placement and other aesthetic settings
+(Fig 1A). Smoothing and re-sampling of images is sometimes required for
+visualisation purposes, which can be achieved via the `ANTsR`
+/`extrantsr` or `fslr` packages.
 
@@
 
-##### *Vertex-level visualisations.*
+##### Vertex-level visualisations.
 
@@
 
-##### *ROI-level visualisations.*
+##### ROI-level visualisations.
 
@@
 
+-   Leged placement and creation
+
 -   For quick and interactive viewing of single images, sometimes GUI
@@
 
--   Although, with `ciftitools`, this becomes easier, as long as
-atlas follows the CIFTI convention.
+-   Although, with `ciftitools`, this becomes easier, as long as atlas
+    follows the CIFTI convention.
 
@@
 -   Have to use complex tools like pyVista
-
-### Figure 1
-
-```{r Figure1 }
-library(patchwork)
-library(ggplot2)
-
-fig1a <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1a.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1b <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1b.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1c <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1c.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1d <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1d.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1e <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1e.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1f <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1f.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1g1 <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1g1.png"),
-                                                        width=ggplot2::unit(1,"npc"),
-                                                        height=ggplot2::unit(1,"npc")))
-fig1g2 <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1g2.png"),
-                                                        width=ggplot2::unit(1,"npc"),
-                                                        height=ggplot2::unit(1,"npc")))
-
-fig1h <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1h.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-fig1i <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG("data/fig1i.png"),
-                                                       width=ggplot2::unit(1,"npc"),
-                                                       height=ggplot2::unit(1,"npc")))
-
-patchwork <- fig1a/fig1b|(fig1c|fig1f)/fig1d|(fig1e|fig1g2)/fig1g1|fig1h/fig1i
-
-patchwork + plot_annotation(tag_levels = 'A',
-                            title = 'Examples of brain visualisations in R')
-
-```
 
@@
 
+#weird angle
+
 library(fsbrain)
@@
                          hemi='both', 
-                         views = 't4',
+                         views = 't9',
                          draw_colorbar = "horizontal",

### 2022-04-02 manuscript.Rmd
figure compiled

@@
 output:
+  word_document: default
   html_document: default
-  word_document: default
   pdf_document: default
@@
     wrap: 72
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
@@
 
-### Figure 1
+\newpage
+\blandscape
 
-```{r Figure1 , echo=FALSE}
+### Figure 1 [Fix image size ratios]
+
+```{r Figure1 , echo=FALSE, out.height = '80%', out.width = '140%'}
 library(patchwork)
@@
 #loop this?
-fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1h', 'fig1i')
+fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1g3','fig1h', 'fig1i')
 figs <- list()
@@
 
-patchwork <- figs[[1]]/figs[[2]]|(figs[[3]]|figs[[6]])/figs[[4]]|(figs[[5]]|figs[[8]])/figs[[7]]|figs[[9]]/figs[[10]]
+patchwork <- figs[[1]]/figs[[2]]|(figs[[3]]|figs[[6]])/figs[[4]]|(figs[[5]]|(figs[[8]]/figs[[9]]))/figs[[7]]|figs[[10]]/figs[[11]]
 
@@
 \
-*[Figure 1 - Add Caption]*
+*[Figure 1 - Add Caption and remove panel F]*
+
+\elandscape
 
@@
 /`extrantsr` or `fslr` packages.
-
-[view_xifti_volume(xii, interactive = TRUE) in cifti tools]
 
@@
 
--   While most of these tools do not require a strond knowledge of
+-   While most of these tools do not require a strong knowledge of
     programming, there can still be a steeper learning curve when
     compared to GUI-based tools.
-
--   Leged placement and creation
 
@@
 
--   But fsbrain has a function;
-    <https://github.com/dfsp-spirit/fsbrain/blob/cb1b9d667a9449b214b20f6420038af2541e48b4/R/vis_dti_tracks.R>)
-
--   For tools which require non-standard or uncommon atlases or ROIs.
-
--   Although, with `ciftitools`, this becomes easier, as long as atlas
-    follows the CIFTI convention.
+-   Lack of user friendly tools which can render non-standard or uncommon atlases or ROIs. Although, with `ciftitools`, this becomes easier, as long as atlas follows the CIFTI convention.
 
 -   3D renderings of non-standard ROIs like unique subcortical schemes
-    or brain stem are still difficult to do.
+    or brain stem are still difficult to do. Can to use complex workarounds like ITKsnap + pyVista.
 
--   Have to use complex tools like pyVista
+### Supplement (Code used to generate figure)
 
@@
   colorbar(breaks,col = hotmetal(n=length(breaks)-1), 
-           text.col = "black", labels = TRUE, maxleft = 0.95) + 
-  title(main = "Voxel Statistic Map")
+           text.col = "black", labels = TRUE, maxleft = 0.95) 
 dev.off()
@@
         NA.x=T, 
-        zlim.y =c(1,300), 
-        mar = c(0.1, 0.1, 1.5, 0.1)) + #marget of bottom, left, top, right borders
-  title("Voxel Atlas Overlay", line = 1.3)
+        zlim.y =c(1,300))
+
+      #  mar = c(0.1, 0.1, 1.5, 0.1)) + #marget of bottom, left, top, right borders
 dev.off()
@@
                    legend_embed = T,
-                   title = "Vertex Statistic Map", 
                    cex.title = 2)
@@
 
-#fig1g <- cowplot::plot_grid(cortex, subcortex, nrow = 1, rel_widths = c(1,.7))
-
 ggsave(filename = 'data/fig1g1.png', plot = cortex, device = 'png', bg = 'white')
 ggsave(filename = 'data/fig1g2.png', plot = subcortex, device = 'png', bg = 'white')
+
+```
+
+```{r, eval=FALSE}
+
+make_ggseg3d <- function(attribute, 
+                         colour.pal = c("light yellow",
+                                        "orange",
+                                        "red",
+                                        "dark red"), 
+                         hide.colourbar=FALSE, 
+                         output.png=FALSE, 
+                         file.name="ggseg_3d.png") {
+  # Inputs: 
+  #' attribute = This must be a numeric vector in this: Left-Thalamus, Left-Caudate, Left-Putamen, Left-Pallidum Left-Hippocampus, Left-Amygdala, Left-Accumbens-area, Right-Thalamus-Proper, Right-Caudate, Right-Putamen, Right-Pallidum, Right-Hippocampus, Right-Amygdala, Right-Accumbens-area
+
+  library(ggseg3d)
+  library(tidyr)
+  library(dplyr)
+  #remove(aseg_3d)
+  aseg_3d <- aseg_3d
+  aseg_3d <- tidyr::unnest(aseg_3d, cols = c(ggseg_3d))
+
+  attribute.ggseg3d <- c(rep(NA, 4), attribute[1:4], rep(NA, 3), attribute[5:7],
+                         rep(NA, 5), attribute[8:14],  rep(NA, 6))
+
+  data <- dplyr::mutate(aseg_3d, attribute =  attribute.ggseg3d)
+  #remove NA regions
+  aseg_3d[which(is.na(data$attribute)),] <- NA
+  aseg_3d <- tidyr::drop_na(aseg_3d)
+
+  data[which(is.na(data$attribute)),] <- NA
+  data <- tidyr::drop_na(data)
+  data$attribute[data$attribute==0]<-NA #make 0 valus NA so they are set as grey in ggseg3d
+
+  scene=list(camera = list(eye = list(x = 0, y = 1, z = -2.25)),
+             aspectratio = list(x=1.6,y=1.6,z=1.6))
+
+  plot <- ggseg3d::ggseg3d(.data = data, 
+                           atlas = aseg_3d, 
+                           colour = "attribute", 
+                           text = "attribute",
+                           palette = colour.pal)
+  plot <- remove_axes(plot)
+  plot <- plotly::layout(plot, 
+                         scene = scene, 
+                         width = 600, height = 600)
+
+  if(hide.colourbar==TRUE){
+    plot <- plotly::hide_colorbar(plot)
+  }
+
+  if( output.png==TRUE){
+    plotly::orca(plot, file =  file.name)
+  }
+
+  return(plot)
+
+}
+
+set.seed(1993)
+volume <- sample(1:20, 14) #randomly generated data for 14 structures
+make_ggseg3d(volume, 
+             colour.pal = c("white", "firebrick"), 
+             output.png = T, file.name = 
+               "data/fig1g3.png")
 

### 2022-04-04 manuscript.Rmd
rep para remove

@@
   word_document: default
+  pdf_document: default
   html_document: default
-  pdf_document: default
 editor_options:
@@
 re-running of code using cloud services (cite).
-
-Neuroimaging data are often spatially 3D and can have multiple time
-points, adding a 4th dimension (e.g. fMRI data). Thus, communicating
-findings or evaluating quality using static 2D slices is challenging.
-While well curated 3D renderings can help with spatial localisation
-(cite madan), in the end, static 2D images can only provide an
-incomplete representation of 3D or 4D data. A added advantage of some of
-code-based tools is that you can generate 'rich' media like interactive
-figures or animations, which can improve scientific communication of
-findings. Many code-based software tools now allow for the generation of
-animated brain visualisations (cite blog) or interactive widgets which
-allow users to zoom, rotate and scroll through slices. Linking to or
-even embedding these videos or interactive figures in papers can greatly
-enhance the communication of findings.
 

### 2022-04-05 manuscript.Rmd
fig update

@@
 functions available in R for visualising voxel, vertex, ROI and
-edge-level data. A more didactic introduction to these tools is provided
-in a [collection of beginner friendly
-R-Notebooks](https://github.com/sidchop/neuRo-vis-BrainHack-2021).
+edge-level data. A didactic introduction to these tools is provided in a
+accompaning [collection of beginner friendly
+R-Notebooks](ttps://github.com/sidchop/neuRo-vis-BrainHack-2021).
 
+```{=tex}
 \newpage
 \blandscape
-
+```
 ### Figure 1 [Fix image size ratios]
@@
 
-#loop this?
 fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1g3','fig1h', 'fig1i')
@@
 
-patchwork <- figs[[1]]/figs[[2]]|(figs[[3]]|figs[[6]])/figs[[4]]|(figs[[5]]|(figs[[8]]/figs[[9]]))/figs[[7]]|figs[[10]]/figs[[11]]
+patchwork <- figs[[1]]/(figs[[2]]|figs[[3]])|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[4]]|figs[[10]]/figs[[11]]
 
@@
 images, colour scales, legend placement and other aesthetic settings
-(Fig 1A). Smoothing and re-sampling of images is sometimes required for
-visualisation purposes, which can be achieved via the `ANTsR`
+(Fig 1A-B). Smoothing and re-sampling of images is sometimes required
+for visualisation purposes, which can be achieved via the `ANTsR`
 /`extrantsr` or `fslr` packages.
@@
 The recently developed `fsbrain` package allows for the visualisation of
-vertex-level and atlas-level data obtained using Freesurfer. It contains
-many flexible functions for visualising individual-level and group-level
-measures such as cortical thickness, volume or surface area (Fig 1B).
-The package also comes with extensive guides and documentations to
-assist users (cite).
+vertex-level and atlas-level data which is derieved using FreeSurfer
+formats. It contains many flexible functions for visualising
+individual-level and group-level measures such as cortical thickness,
+volume or surface area (Fig 1E). The package also comes with extensive
+guides and documentations to assist users (cite).
 
@@
 structural and functional imaging data, as it combines vertex-level data
-of the cortex with voxel-level data fo the cerebellum and sub-cortex. In
-R, CIFTI data can now be read, visualised and manipulated using the
-well-documented `ciftiTools` package (Fig 1C; cite).
+of the cortex with voxel-level data for the cerebellum and sub-cortex.
+In R, CIFTI data can now be read, visualised and manipulated using the
+well-documented `ciftiTools` package (Fig 1C-D,F; cite).
 
@@
 packages such as `gganimate`, enabling users to animate and visualise
-dynamic changes in spatial and temporal statistics across ROIs. The
-`ciftiTools` package also allows for surface and voxel-level
+dynamic changes in spatial and temporal statistics across ROIs.
+
+The `ciftiTools` package also allows for surface and voxel-level
 visualisation of ROIs for the cortex and sub-cortex respectively (Fig
@@
 
--   Lack of user friendly tools which can render non-standard or uncommon atlases or ROIs. Although, with `ciftitools`, this becomes easier, as long as atlas follows the CIFTI convention.
+-   Lack of user friendly tools which can render non-standard or
+    uncommon atlases or ROIs. Although, with `ciftitools`, this becomes
+    easier, as long as atlas follows the CIFTI convention.
 
 -   3D renderings of non-standard ROIs like unique subcortical schemes
-    or brain stem are still difficult to do. Can to use complex workarounds like ITKsnap + pyVista.
+    or brain stem are still difficult to do. Can to use complex
+    workarounds like ITKsnap + pyVista.
 
@@
 # ADD COMMENTS TO EXPLAIN EACH LINE
-
 library(neurobase)
@@
        NA.x = T, 
-       col.y= hotmetal(), 
+       col.y= viridis::viridis(n = 500), 
        xyz = c(70,50,80),
@@
        mfrow = c(1,3)) +
-  colorbar(breaks,col = hotmetal(n=length(breaks)-1), 
+  colorbar(breaks,col =viridis::viridis(n=length(breaks)-1), 
            text.col = "black", labels = TRUE, maxleft = 0.95) 
@@
 # Load the package and point to the Connectome Workbench
-suppressPackageStartupMessages(library(ciftiTools))
+library(ciftiTools)
 
@@
 surfL_fname <- ciftiTools.files()$surf["left"]
+surfR_fname <- ciftiTools.files()$surf["right"]
 
 cii <- read_cifti(
-  cifti_fname, brainstructures="left", 
-  surfL_fname=surfL_fname)
+  cifti_fname, brainstructures="all", 
+  surfL_fname=surfL_fname,
+  surfR_fname=surfR_fname)
 
@@
 
-#weird angle
-
 library(fsbrain)
@@
 #download_optional_data()
-subjects_dir = get_optional_data_filepath("subjects_dir")
+#download_fsaverage(accept_freesurfer_license = TRUE)
 
-subject_id = 'subject1'
+subjects_dir <- get_optional_data_filepath("subjects_dir")
 
-colourmap = colorRampPalette(viridis::viridis(n = 100))
+subject_id <- 'subject1'
 
-vis.subject.morph.native(subjects_dir = subjects_dir, 
-                         subject_id = 'subject1', 
-                         measure = 'thickness', 
-                         hemi='both', 
-                         views = 't9',
-                         draw_colorbar = "horizontal",
-                         cortex_only = T, surface = "white", 
+colourmap <- colorRampPalette(viridis::viridis(n = 10000))
+fsbrain.set.default.figsize(700, 700);
+
+cm = vis.subject.morph.standard(subjects_dir, 
+                                subject_id, 'sulc', 
+                                fwhm='10', 
+                                cortex_only = T, 
+                                views=NULL, 
                                 makecmap_options = list('colFn'=colourmap))
+img = export(cm, colorbar_legend='Effect', output_img = "data/fig1d.png")
+
 rgl.snapshot("data/fig1d.png")
@@
                             borders = "black", 
-                            hemisphere = "left", )
+                            hemisphere = "both",
+                            view = 'lateral')
 
@@
                    .data = sub_base_atlas,
-                   hemisphere = "right",
                    mapping=aes(fill=Effect), 
-                   position="stacked",
+                   position = "dispersed",
                    colour="black",
+                   hemi =c('left', 'right'),
                    size=.2,
@@
 make_ggseg3d(volume, 
-             colour.pal = c("white", "firebrick"), 
-             output.png = T, file.name = 
-               "data/fig1g3.png")
+             colour.pal = viridis::viridis(n=length(volume)), 
+             output.png = T, file.name = "data/fig1g3.png")
 

### 2022-04-05 manuscript.Rmd
fig up2

@@
   word_document: default
+  html_document: default
   pdf_document: default
-  html_document: default
 editor_options:

### 2022-04-05 manuscript.Rmd
sp

@@
 useful starting point and reduce the decision burden on the user.
-However, similar pre-sets are often available in the from of default
+However, similar pre-sets are often available in the form of default
 settings in most code-based packages, negating the need for the user to

### 2022-04-12 manuscript.Rmd
fix1a

@@
 ---
-title: "Reproducible and programmatic generation of neuroimaging visualisations"
-author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
+title: "Reproducible and programmatic generation of neuroimaging visualizations"
+author: "Sidhant Chopra, Loïc Labache, Winnie Orchard, Avram Holmes"
 date: "09/03/2022"
 output:
+  pdf_document: default
+  html_document: default
   word_document: default
-  html_document: default
-  pdf_document: default
 editor_options:
@@
 
-Visualising neuroimaging data is one of the primary ways in which we
-evaluate data quality, interpret results and communicate findings. These
-visualisations are commonly produced using graphic interface-based (GUI)
-tools where individual images are opened and display settings are
-manually changed until the desired output is reached. The choice to use
-GUI-based software's has been driven by a perception of convenience,
-flexibility and accessibility. However now there are also many
-code-based software packages which are well-documented and don't often
-require high-level knowledge of programming, making them more accessible
-to the neuroimaging community. These tools are flexible and allow for
-the generation of reproducible, high-quality and publication-ready brain
-visualisations in only a few lines of code (Figure 1), especially within
-the R, Python and Matlab environments.
+The visualization of neuroimaging data is one of the primary ways in
+which we evaluate data quality, interpret results, and communicate
+findings. These visualizations are commonly produced using graphic
+interface-based (GUI) tools where individual images are opened and,
+within each instance, display settings are manually changed until the
+desired output is reached. In large part, the choice to use GUI-based
+software has been driven by a perception of convenience, flexibility,
+and accessibility. However now there are also many code-based software
+packages which are well-documented and do not often require high-level
+knowledge of programming, making them more accessible to the
+neuroimaging community. These tools are flexible and allow for the
+generation of reproducible, high-quality, and publication-ready brain
+visualizations in only a few lines of code (Figure 1), especially within
+the R, Python and MATLAB environments.
 
 This article will cover three major advantages of using code-generated
-visualisations over GUI based tools: replicability, flexibility and
+visualizations over GUI based tools: replicability, flexibility, and
 integration. First, by generating figures using code, you increase the
@@
 readers. Second, code-based software provides more precise controls over
-visualisation settings, while also benefiting from advantages of
-programming, such as being able to iteratively generate multiple
-figures. Finally, being able to integrate figure generation into your
-analysis scripts reduces chances of errors, with more advanced tools now
-allowing for seamless weaving together of prose and code. Here, we
-review the advantages of learning and using programmatic neuroimaging
-visualisations, focusing on benefits to replicability, flexibility and
-intergration. We conclude by introducing examples of R-packages which
-allow for visualisation of statistics at region-of-interest (ROI),
-voxel, vertex and edge level data, followed by a brief discussion of
-limitations and functionality gaps in code-based brain visualisation
+display settings, while also benefiting from advantages of programming,
+such as being able to iteratively and rapidly generate multiple figures.
+Finally, being able to integrate figure generation into your analysis
+scripts reduces chances of errors and increases the accessibility of
+resulting analyses pipeline, with more advanced tools now allowing for
+the seamless integration of prose and code. Here, we review the
+advantages of learning and using programmatic neuroimaging
+visualizations, focusing on benefits to replicability, flexibility and
+integration. We conclude by introducing examples of R-packages which
+allow for visualization of statistics at region-of-interest (ROI),
+voxel, vertex, and edge level data, followed by a brief discussion of
+limitations and functionality gaps in code-based brain visualization
 tools.
@@
 scientific output which can be transparently evaluated and independently
-replicated. In practise, what this usually means is openly sharing
-detailed methods, materials, code and data. While there is a trend
-towards increasing transparency and code sharing in neuroimaging
-research (cite), the sharing of code used to generate figures which
-include brain renderings and spatial maps has been relatively neglected.
-This gap in reproducibility is partly driven by the fact that brain
-figures are often created using a manual process of tinkering with
-sliders, buttons and overlays on a GUI, concluding with a screenshot and
-sometimes beatification in image processing software like Illustrator.
-This process inherently makes neuroimaging visualisations difficult, if
-not impossible to replicate, even by the authors who created them.
+replicated. In practice, this typically entails openly sharing detailed
+methods, materials, code, and data. While there is a trend towards
+increasing transparency and code sharing in neuroimaging research
+(cite), the sharing of code used to generate figures which include brain
+renderings and spatial maps has been relatively neglected. This gap in
+reproducibility is partly driven by the fact that brain figures are
+often created using a manual process that involves tinkering with
+sliders, buttons, and overlays on a GUI, concluding with a screenshot
+and sometimes beautification in image processing software like
+Illustrator. This process inherently makes neuroimaging visualizations
+difficult, if not impossible to replicate, even by the authors
+themselves.
 
-Given that brain figures regularly form the centrepiece of
-interpretation within a paper, conference presentations and news
-reports, making sure they can be reliably regenerated is crucial for
-knowledge generation. By writing and sharing code used to generate brain
-visualisations, a direct and traceable link is established between the
-underlying data and scientific figure. While the code that produces a
-replicable figure doesn't reflect the validity of the scientific finding
-or the accuracy of the content figure, it instils transparency and
-robustness while demonstrating a desire to further scientific knowledge.
-Some would even consider publishing figures which cannot be replicated
-as closer to advertising, rather than science (cite blog).
+Visualization scripts should reflect a core feature of open science.
+Given that brain figures regularly form the centerpiece of
+interpretation within papers, conference presentations, or news reports,
+making sure they can be reliably regenerated is crucial for knowledge
+generation. By writing and sharing code used to generate brain
+visualizations, a direct and traceable link is established between the
+underlying data and the corresponding scientific figure. While the code
+that produces a replicable figure doesn't necessarily reflect the
+validity of the scientific finding or the accuracy of the associated
+content, it allows for reproducibility, instilling transparency and
+robustness, while demonstrating a desire to further scientific
+knowledge. Some even consider publishing figures which cannot be
+replicated as closer to advertising, rather than science (cite blog).
 
@@
 
-Being able to exactly replicate your figures via code has serious
-advantages beyond good open science practises. In particular, the
+Being able to exactly replicate your figures via code has marked
+advantages beyond good open science practices. In particular, the
 ability to reprogram inputs (such as statistical maps) and settings
-(such as colour schemes and visual orientations) can streamline your
-entire scientific workflow. Changing inputs and settings via code allows
-for the easy production of multiple figures, such as those resulting
-from multiple analyses which require similar visualisations. While some
-GUI-based tools do offer command-line access to generate visualisations,
-they can lack flexibility to easily generate publication ready figures
-and can lose the benefits, such as iteration, provided by your preferred
-programming environment. A simple for-loop or copying and pasting the
-code with the input and/or setting-of-interest modified can be a
-powerful method for exploring visualisation options or creating
-multi-panel figures. Likewise, an arduous request from a reviewer to
-alter the data processing or analysis becomes less of a burden when the
-figure can be re-generated with a few lines of code, as opposed to
-re-pasting and re-illustrating them. Having a code-base with
-reprogrammable inputs can mean that the generation of visualisations
-requires less time, energy and effort than manual GUI-based generation.
-This also makes it easier to make figures for each subsequent project
-that you work on. Keep in mind that the gains of writing code for your
-figures are cumulative, and in addition to improving your programming,
-you start to build a code-base for figure generation that you can
-continue to reuse and share through your scientific career.
+(such as color schemes, thresholds, and visual orientations) can
+streamline your entire scientific workflow. Changing inputs and settings
+via code allows for the easy production of multiple figures, such as
+those resulting from multiple analyses which require similar
+visualizations. While some GUI-based tools have historically offered
+command-line access to generate replicable visualizations, they can lack
+both the flexibility to easily generate publication ready figures and
+the benefits, such as iteration, provided by your preferred programming
+environment. A simple for-loop or copying and pasting the code with the
+input and/or setting-of-interest can be a powerful method for exploring
+visualization options or rapidly creating multi-panel figures. Likewise,
+an arduous request from a reviewer or collaborator to alter the
+pre-processing or analysis becomes less of a burden when the associated
+figures can be re-generated with a few lines of code, as opposed to
+re-pasting and re-illustrating them manually. Having a code-base with
+modifiable inputs can mean that the generation of visualizations
+requires less time, energy and effort than image and instance specific
+GUI-based generation. This also makes it easier to generate consistent
+figures across subsequent projects. Keep in mind that the gains of
+writing code for your figures are cumulative, and in addition to
+improving your programming, you start to build a code-base for figure
+generation that you can continue to reuse and share throughout your
+scientific career.
 
-Precise controls via code over visualization settings, such as colour
+Precise controls via code over visualization settings, such as color
 schemes, legend placement and camera angles, can provide you with much
-greater flexibility over visualisations. Nonetheless, part of the appeal
-of GUI-based tools is that the pre-sets for such settings can provide a
-useful starting point and reduce the decision burden on the user.
-However, similar pre-sets are often available in the form of default
-settings in most code-based packages, negating the need for the user to
-manually enter each and every choice of setting required for making the
-image. Most code-based tools also come with detialed documentation, or
-even entire papers (cite ggseg and ciftitools) which provide examples of
-figures which can be used as starting points or templates for new users.
-As the popularity of code-sharing for figure increases, there will be an
-cornucopia of templates that can be used as starting points for new
-figures.
+greater flexibility over visualizations. Nonetheless, part of the appeal
+of GUI-based tools is that the presets for such settings can provide a
+useful starting point and reduce the decision burden on novice users.
+However, similar presets are often available in the form of default
+settings across most code-based packages, negating the need for the user
+to manually enter each and every choice of setting required for creating
+an image. Most code-based tools also come with documentation, with
+R-packages on the CRAN or **Neuroconductor** repositories having
+compulsory requirements for detailed guidance. Recent packages have even
+started to include documentation in GitHub repositories, or even entire
+papers (cite ggseg and ciftitools) which provide examples of figures
+which can be used as starting points or templates for new users. As the
+popularity of code-sharing for figure increases, there will be a
+cornucopia of templates that can be used as the basis for new figures.
 
-While brain visualisations are often thought of as the end results of
-analyses, they also form a vital part of quality control of imaging
+While brain visualizations are often thought of as the end results of
+analyses, they also form a vital part of quality control for imaging
 data. Tools to automatically detect artefacts, de-noise the data and
 generate derivatives are becoming more robust, but we are not yet at the
-stage where visualising the data during processing is no longer need.
-Nonetheless, when working with large datasets such as Human Connectome
-Project (cite) or UK BioBank (cite), it is unfeasible to use traditional
-GUI-based tool to visually check the data. The time it takes to open a
-single file and achieve the desired visualisation settings vastly
-compounds when working with large datasets. Knowing how to
-programmatically generate brain visualisations can allow you to iterate
-your visualisation code over each image of a large datasets making
+stage where visualizing the data during processing is no longer
+necessary. Nonetheless, when working with large datasets such as Human
+Connectome Project (cite) or UK BioBank (cite), it is unfeasible to use
+traditional GUI-based tool to visually check the data. The time it takes
+to open a single file and achieve the desired visualization settings
+vastly compounds when working with large datasets. Knowing how to
+programmatically generate brain visualizations can allow you to iterate
+your visualization code over each image of a large datasets making
 checking the quality of each data processing or analysis step accessible
@@
 
-Often programming languages such as R, Python and Matlab are used for
-the analysis in neuroimaging studies, but the brain visualisation
-resulting from these analyses is outsourced to separate GIU-based
-visualisation tools such as FSLeyes, Freeview or ITK-snap. Switching
-from your analysis environment to a GUI-based visualisation process be a
-cumbersome deviation from the scientific workflow. This can make
-debugging errors more difficult, as you have to regularly switch program
-to visually examine the results of any modifications to analyses. Using
-the brain visualisation tools that already exist within your chosen
-programming environment can provide instant visual feedback on the
-impact of modifications to processing or analyses.
+Often programming languages such as R, Python and MATLAB are used for
+the analysis and non-brain visualizations in neuroimaging studies, but
+the brain visualizations resulting from these analyses are outsourced to
+separate GIU-based visualization tools such as FSLeyes, Freeview or
+ITK-snap. Switching from your analysis environment to a GUI-based
+visualization process be a cumbersome deviation from the scientific
+workflow. This can make debugging errors more difficult, as you have to
+regularly switch program to visually examine the results of any
+modifications or adjustments to prior analyses. Using the brain
+visualization tools that already exist within your chosen programming
+environment can provide instant visual feedback on the impact of
+modifications to processing or analyses.
 
@@
 code-based tools available within your preferred environment, brain
-visualisations can be directly integrated and embedded within a paper or
+visualizations can be directly integrated and embedded within a paper or
 report. Some journals that publish neuroimaging studies are moving
 towards allowing reproducible manuscripts, including reproducible
-figures (cite e-life,f1000,plos), with some even allowing on-demand
+figures (cite e-life, f1000,plos), with some even allowing on-demand
 re-running of code using cloud services (cite).
@@
 Neuroimaging data are often spatially 3D and can have multiple time
-points, adding a 4th dimension (e.g. fMRI data). Thus, communicating
+points, adding a 4th dimension (e.g., fMRI data). Thus, communicating
 findings or evaluating quality using static 2D slices is challenging,
@@
 incomplete representation of the data, and forces researchers to choose
-the best angle to show, which often involves compromising one result for
-another. An added advantage of some of the code-based tools is that you
-can generate 'rich' media like interactive widgets -- figures or
-animations, which allow users to zoom, rotate and scroll through slices.
-Interacting with a figure in this way can improve scientific
-communication of findings. Linking to or even embedding these videos or
-interactive figures in papers can greatly enhance the communication of
-findings and make your paper more engaging for the reader. Such rich
-brain visualisations lend themselves to being embedded or shared on
-science communication mediums other than academic papers - such as
-presentations, web-sites and social media - all of which can promote the
-communication of your research with peers and a reach larger audiences.
+the "best" angle to show, which often involves compromising one result
+to emphasize another. An added advantage of some of the code-based tools
+is that you can generate 'rich' media like interactive widgets --
+figures or animations, which allow users to zoom, rotate and scroll
+through slices. Interacting with a figure in this way can improve
+scientific communication of findings. Linking to or even embedding these
+videos or interactive figures in papers can greatly enhance the
+communication of findings and make your paper more engaging for the
+reader. Such rich brain visualizations lend themselves to being embedded
+or shared on science communication mediums other than academic papers -
+such as presentations, websites and social media - all of which can
+promote the communication of your research with peers and a reach larger
+audiences. This last point is becoming increasingly saliet, as marketing
+science on social media has become a core medium for the spreading
+discoveries, science communication and even a primary avenue for
+obtaining employment for early-career re (Cite?). Overall, public
+engagement, whether it is a researcher, a member of a jury or civil
+society, is one of the keystones of science, and the images we create
+are at the center of the process (Li and Xie, 2020:
+10.1177/0022243719881113).
 
-### Examples of neuroimaging visualisation packages available in R
+### Examples of neuroimaging visualization packages available in R
 
 The following four sections provide brief examples packages and
-functions available in R for visualising voxel, vertex, ROI and
+functions available in R for visualizing voxel, vertex, ROI and
 edge-level data. A didactic introduction to these tools is provided in a
-accompaning [collection of beginner friendly
-R-Notebooks](ttps://github.com/sidchop/neuRo-vis-BrainHack-2021).
+accompanying [collection of beginner friendly
+R-Notebooks](ttps://github.com/sidchop/neuRo-vis-BrainHack-2021). This
+is not an exhaustive list of packages available for visualizing brain
+data in R, rather, the following sections and accompanying notebooks aim
+to give the reader a sense of the available options.
 
@@
 ```
-### Figure 1 [Fix image size ratios]
-
 ```{r Figure1 , echo=FALSE, out.height = '80%', out.width = '140%'}
@@
 
-patchwork <- figs[[1]]/(figs[[2]]|figs[[3]])|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[4]]|figs[[10]]/figs[[11]]
+patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[4]]|(figs[[3]]/figs[[10]]/figs[[11]])
 
@@
 patchwork + plot_annotation(tag_levels = 'A',
-                            title = 'Examples of brain visualisations in R')
+                            title = 'Examples of brain visualizations in R')
 
@@
 \
-*[Figure 1 - Add Caption and remove panel F]*
+*Figure 1. Examples of brain imaging visualization make in using
+different R-packages.* A) Voxel-based statistical map threshold and
+overlaid over a T1-weighted template data, with a single axial slice
+shown. Made using the the `ortho2` function from the `neurobase`
+package. B) A voxel-level cortical parcellation overlaid on T1-weighted
+MRI data shown in 9-slice axial orientation. Made using the `overlay`
+function from the `neurobase` package. C) A CIFTI format surface atlas
+with a corresponding statistic assigned to each regions, with both
+hemispheres displayed on a inflated template surface in lateral view.
+Made using the `view_xifti_surface` from the `ciftiTools` package. D) A
+coronal cross-sectional rendering of X, where a statisitcal alue has
+been assigned to each of the X regions.
 
@@
 
-##### Voxel-level visualisations.
+##### Voxel-level visualizations.
 
 The `oro.nifti` package allows for the reading, writing, manipulation
-and visualisation of voxel-level imaging data of either nifti, analyze
+and visualization of voxel-level imaging data of either nifti, analyze
 or afni formats. In particular, the `image`, `slice` and `orthographic`
@@
 (Fig 1A-B). Smoothing and re-sampling of images is sometimes required
-for visualisation purposes, which can be achieved via the `ANTsR`
+for visualization purposes, which can be achieved via the `ANTsR`
 /`extrantsr` or `fslr` packages.
 
-##### Vertex-level visualisations.
+##### Vertex-level visualizations.
 
-The recently developed `fsbrain` package allows for the visualisation of
+The recently developed `fsbrain` package allows for the visualization of
 vertex-level and atlas-level data which is derieved using FreeSurfer
@@
 
-##### ROI-level visualisations.
+##### ROI-level visualizations.
 
@@
 The `ciftiTools` package also allows for surface and voxel-level
-visualisation of ROIs for the cortex and sub-cortex respectively (Fig
+visualization of ROIs for the cortex and sub-cortex respectively (Fig
 1E). Flexibly allowing CIFTI format atlases and ROIs to be displayed.
 
-##### Edge-level visualisations.
+##### Edge-level visualizations.
 
@@
 
-### Limitations and functionality gaps in R packages for brain visualisation
+### Limitations and functionality gaps in R-packages for brain visualization
 
--   While most of these tools do not require a strong knowledge of
-    programming, there can still be a steeper learning curve when
-    compared to GUI-based tools.
+Most of these tools introduced above do not require a strong
+knowledge of programming, but there is still a steeper learning curve
+when compared to GUI-based tools. This is especially true when learning
+to making fine adjustments to visual auxiliary such as legend placement,
+font size and multi-panel figure positioning, for the purpose of a publication
+ready figure. While most tools offer some control over these finer
+steps, there are differences between them in feature availability and
+usability. Although some interactive widgets with limited functionality 
+exist (cite papyr), for quick and interactive viewing of single images, 
+sometimes GUI tool scan be faster and for convenience, can sometimes be 
+opened directly from within some programming environments.
 
--   For quick and interactive viewing of single images, sometimes GUI
-    tools can be faster (although, fsleyes can be called from python and
-    R environments with ease)
+[surface projections]
 
--   Visualising data-types such as streamlines from DWI-based
-    tractography are still not well represented in code-based tools.
-
--   Lack of user friendly tools which can render non-standard or
-    uncommon atlases or ROIs. Although, with `ciftitools`, this becomes
-    easier, as long as atlas follows the CIFTI convention.
-
--   3D renderings of non-standard ROIs like unique subcortical schemes
-    or brain stem are still difficult to do. Can to use complex
-    workarounds like ITKsnap + pyVista.
+Some data types are still not well represented in code-based tools. In 
+particular, visualizing streamlines resulting from DWI-based, although 
+some progress is being made (see XXX? - dont know). Similarly, visualizing 
+custom ROIs as 3D renderings, such as those resuting from voxels within 
+subcortex or brain stem, is not yet straight forwared.
 
@@
 #Figure 1A
-#voxel 1
 
-# ADD COMMENTS TO EXPLAIN EACH LINE
 library(neurobase)
@@
 
+#Load in a nifti (.nii.gz) file of a standardized template so use as a background. 
 template <- readnii('data/MNI152_T1_1mm_brain.nii.gz') #load the nifti file into R
 
+#Load in a nifti (.nii.gz) file of the statistic you wanted of overlay, with the same dimensions as the template.  
 effect <- readnii("data/MNI152_effect_size.nii.gz")
 
-#threshold the effect at the desired cut-off
+#Threshold the statistic map so only values about a specified amount are displayed
 effect[effect<0.3] <- NA
 
-#Plot the effect on the brain template
+#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)
 breaks = seq(.3,.6, by=0.005)
 
+#[Optional] If you want to output the figure as a .png, open a png image device
 png("data/fig1a.png")
-ortho2(x = template, 
-       y = effect, 
-       crosshairs = F, 
-       bg = "white", 
-       NA.x = T, 
-       col.y= viridis::viridis(n = 500), 
-       xyz = c(70,50,80),
-       useRaster = T,
-       ycolorbar = TRUE, 
-       mfrow = c(1,3)) +
-  colorbar(breaks,col =viridis::viridis(n=length(breaks)-1), 
-           text.col = "black", labels = TRUE, maxleft = 0.95) 
+
+#Use the ortho2 function from the neurobase package to make the figure
+ortho2(x = template,   #Specify the background template
+       y = effect,     #Specify the effect you want to overlay on the tempplate
+       crosshairs = F, #Remove the cross-hairs
+       bg = "white",   #Make the background white 
+       NA.x = T,       #Do not display NA values
+       col.y= viridis::viridis(n = 500), #Select the colour scale. In this case I have used the viridis scale from the viridis package. 
+       xyz = c(70,50,80), #set the x y & z slice you want to visualise
+       useRaster = T,   #Sometimes using Raster makes for clearer plots
+       ycolorbar = TRUE, #Add a colorbar
+       mfrow = c(1,1)) + 
+  colorbar(breaks,col = viridis::viridis(n=length(breaks)-1), 
+           text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar
+
 dev.off()
@@
 
-dti <- readnii('data/sub-001__t1_warped.nii.gz') #load the nifti file into R
+#Load in a nifti (.nii.gz) file to use as a background. 
+t1 <- readnii('data/sub-001__t1_warped.nii.gz')
 
@@
 png('data/fig1b.png')
-overlay(x=robust_window(dti), y=atlas, 
+overlay(x=robust_window(t1), y=atlas, 
         plot.type = "single", 
@@
 view_xifti_surface(cii, 
-                   hemisphere = "left", 
-                   view = "both", 
+                   hemisphere = "both", 
+                   view = "lateral", 
                    idx = 1,
                    colors = viridis::viridis(n = 100),
-                   zlim = c(1,1.5),  
+                   zlim = c(1.2,1.5),  
                    legend_embed = T,
@@
                    edge.color = scale_edge_colour_gradient2(low='yellow', mid='orange', high='red')) 
-ggsave(filename = 'data/fig1h.png', plot = fig1h, device = 'png', bg = 'white')
+ggsave(filename = 'data/fig1h.png', 
+       plot = fig1h, 
+       device = 'png',
+       bg = 'white',
+       height = 7, 
+       units = "in")
 

### 2022-04-21 manuscript.Rmd
manuscript updated

@@
 ---
-title: "Reproducible and programmatic generation of neuroimaging visualizations"
-author: "Sidhant Chopra, Loïc Labache, Winnie Orchard, Avram Holmes"
-date: "09/03/2022"
+title: Reproducible and programmatic generation of neuroimaging visualizations
+authors:
+  - name: Sidhant Chopra
+    thanks: Corresponding author
+    department: Department of Psychology
+    affiliation: Yale University
+    location: CT, USA, 06511
+    email: sidhant.chopra@yale.com
+  - name: Loïc Labache
+    department: School of Psychology
+    affiliation: Department of Psychology
+    location: CT, USA, 06511
+  - name: Edwina R Orchard
+    department: School of Psychology
+    affiliation: Department of Psychology
+    location: CT, USA, 06511
+  - name: Avram Holmes
+    department: School of Psychology
+    affiliation: Department of Psychology
+    location: CT, USA, 06511
+abstract: Add words here. 
+keywords:
+  - Brain Visualization
+  - MRI Visualization
 output: 
-  pdf_document: default
-  html_document: default
-  word_document: default
-editor_options:
-  markdown:
-    wrap: 72
+  bookdown::pdf_book:
+    base_format: rticles::arxiv_article
+    keep_tex: true
+    latex_engine: xelatex
+  bookdown::word_document2:
+    toc: false
+linestretch: 2
 header-includes:
@@
 - \newcommand{\elandscape}{\end{landscape}}
+- \usepackage{setspace}\doublespacing
 ---
@@
 
-### Introduction
+# Introduction
 
-The visualization of neuroimaging data is one of the primary ways in
-which we evaluate data quality, interpret results, and communicate
-findings. These visualizations are commonly produced using graphic
-interface-based (GUI) tools where individual images are opened and,
-within each instance, display settings are manually changed until the
-desired output is reached. In large part, the choice to use GUI-based
-software has been driven by a perception of convenience, flexibility,
-and accessibility. However now there are also many code-based software
-packages which are well-documented and do not often require high-level
-knowledge of programming, making them more accessible to the
-neuroimaging community. These tools are flexible and allow for the
-generation of reproducible, high-quality, and publication-ready brain
-visualizations in only a few lines of code (Figure 1), especially within
-the R, Python and MATLAB environments.
+The visualization of neuroimaging data is one of the primary ways in which we evaluate data quality, interpret results, and communicate findings.
+These visualizations are commonly produced using graphic interface-based (GUI) tools where individual images are opened and, within each instance, display settings are manually changed until the desired output is reached.
+In large part, the choice to use GUI-based software has been driven by a perception of convenience, flexibility, and accessibility.
+However, there now exists many code-based software packages which are well-documented and do not often require high-level knowledge of programming, making them more accessible to the neuroimaging community (Table 1).
+These tools are flexible and allow for the generation of reproducible, high-quality, and publication-ready brain visualizations in only a few lines of code (Figure 1), especially within the R, Python and MATLAB environments.
 
-This article will cover three major advantages of using code-generated
-visualizations over GUI based tools: replicability, flexibility, and
-integration. First, by generating figures using code, you increase the
-replicability of your figures for yourself, your collaborators and your
-readers. Second, code-based software provides more precise controls over
-display settings, while also benefiting from advantages of programming,
-such as being able to iteratively and rapidly generate multiple figures.
-Finally, being able to integrate figure generation into your analysis
-scripts reduces chances of errors and increases the accessibility of
-resulting analyses pipeline, with more advanced tools now allowing for
-the seamless integration of prose and code. Here, we review the
-advantages of learning and using programmatic neuroimaging
-visualizations, focusing on benefits to replicability, flexibility and
-integration. We conclude by introducing examples of R-packages which
-allow for visualization of statistics at region-of-interest (ROI),
-voxel, vertex, and edge level data, followed by a brief discussion of
-limitations and functionality gaps in code-based brain visualization
-tools.
+This article will cover three major advantages of using code-generated visualizations over GUI based tools: replicability, flexibility, and integration.
+First, by generating visualizations using code, you increase the replicability of your figures for yourself, your collaborators and your readers.
+Second, code-based tools provides more precise controls over display settings, while also benefiting from advantages of programming, such as being able to iteratively and rapidly generate multiple figures.
+Finally, being able to integrate figure generation into your analysis scripts reduces chances of errors and increases the accessibility of resulting analyses pipeline, with more advanced tools now allowing for the seamless integration of prose and code.
+Here, we review the advantages of learning and using programmatic neuroimaging visualizations, focusing on benefits to replicability, flexibility and integration.
+We conclude by introducing examples of R-packages which allow for visualization of statistics at region-of-interest (ROI), voxel, vertex, and edge level data, followed by a brief discussion of limitations and functionality gaps in code-based brain visualization tools.
 
-### Replicability
+# Replicability
 
-In recent years, there have been multiple large-scale efforts
-empirically demonstrating the lack of reproducibility of findings from
-neuroimaging data (cite poldrack). One common solution proposed for
-achieving robust and reliable discoveries has been to encourage
-scientific output which can be transparently evaluated and independently
-replicated. In practice, this typically entails openly sharing detailed
-methods, materials, code, and data. While there is a trend towards
-increasing transparency and code sharing in neuroimaging research
-(cite), the sharing of code used to generate figures which include brain
-renderings and spatial maps has been relatively neglected. This gap in
-reproducibility is partly driven by the fact that brain figures are
-often created using a manual process that involves tinkering with
-sliders, buttons, and overlays on a GUI, concluding with a screenshot
-and sometimes beautification in image processing software like
-Illustrator. This process inherently makes neuroimaging visualizations
-difficult, if not impossible to replicate, even by the authors
-themselves.
+In recent years, there have been multiple large-scale efforts empirically demonstrating the lack of reproducibility of findings from neuroimaging data (Poldrack et al., 2017).
+One common solution proposed for achieving robust and reliable discoveries has been to encourage scientific output which can be transparently evaluated and independently replicated.
+In practice, this typically entails openly sharing detailed methods, materials, code, and data.
+While there is a trend towards increasing transparency and code sharing in neuroimaging research, the sharing of code used to generate figures which include brain renderings and spatial maps has been relatively neglected.
+This gap in reproducibility is partly driven by the fact that brain figures are often created using a manual process that involves tinkering with sliders, buttons, and overlays on a GUI, concluding with a screenshot and sometimes beautification in image processing software like Illustrator or Photoshop.
+Such a process inherently makes neuroimaging visualizations difficult, if not impossible to replicate, even by the authors themselves.
 
 Visualization scripts should reflect a core feature of open science.
-Given that brain figures regularly form the centerpiece of
-interpretation within papers, conference presentations, or news reports,
-making sure they can be reliably regenerated is crucial for knowledge
-generation. By writing and sharing code used to generate brain
-visualizations, a direct and traceable link is established between the
-underlying data and the corresponding scientific figure. While the code
-that produces a replicable figure doesn't necessarily reflect the
-validity of the scientific finding or the accuracy of the associated
-content, it allows for reproducibility, instilling transparency and
-robustness, while demonstrating a desire to further scientific
-knowledge. Some even consider publishing figures which cannot be
-replicated as closer to advertising, rather than science (cite blog).
+Given that brain figures regularly form the centerpiece of interpretation within papers, conference presentations, or news reports, making sure they can be reliably regenerated is crucial for knowledge generation.
+By writing and sharing code used to generate brain visualizations, a direct and traceable link is established between the underlying data and the corresponding scientific figure.
+While the code that produces a replicable figure doesn't necessarily reflect the validity of the scientific finding or the accuracy of the associated content, it allows for reproducibility, instilling transparency and robustness, while demonstrating a desire to further scientific knowledge.
+Some even consider publishing figures which cannot be replicated as closer to advertising, rather than science (Steel, 2013).
 
-### Flexibility
+While some GUI-based tools have historically offered command-line access to generate replicable visualizations, they can lack both the flexibility to easily generate publication ready figures and the benefits, such as iteration, provided by your preferred programming environment.
+Likewise, other GUI-based tools offer replicability in the form of automatically generated batch scripts or in-built terminals, which are often idiosyncratic and lack documentation to make them easily usable or reproducible by those not familiar with the specific software.
 
-Being able to exactly replicate your figures via code has marked
-advantages beyond good open science practices. In particular, the
-ability to reprogram inputs (such as statistical maps) and settings
-(such as color schemes, thresholds, and visual orientations) can
-streamline your entire scientific workflow. Changing inputs and settings
-via code allows for the easy production of multiple figures, such as
-those resulting from multiple analyses which require similar
-visualizations. While some GUI-based tools have historically offered
-command-line access to generate replicable visualizations, they can lack
-both the flexibility to easily generate publication ready figures and
-the benefits, such as iteration, provided by your preferred programming
-environment. A simple for-loop or copying and pasting the code with the
-input and/or setting-of-interest can be a powerful method for exploring
-visualization options or rapidly creating multi-panel figures. Likewise,
-an arduous request from a reviewer or collaborator to alter the
-pre-processing or analysis becomes less of a burden when the associated
-figures can be re-generated with a few lines of code, as opposed to
-re-pasting and re-illustrating them manually. Having a code-base with
-modifiable inputs can mean that the generation of visualizations
-requires less time, energy and effort than image and instance specific
-GUI-based generation. This also makes it easier to generate consistent
-figures across subsequent projects. Keep in mind that the gains of
-writing code for your figures are cumulative, and in addition to
-improving your programming, you start to build a code-base for figure
-generation that you can continue to reuse and share throughout your
-scientific career.
+# Flexibility
 
-Precise controls via code over visualization settings, such as color
-schemes, legend placement and camera angles, can provide you with much
-greater flexibility over visualizations. Nonetheless, part of the appeal
-of GUI-based tools is that the presets for such settings can provide a
-useful starting point and reduce the decision burden on novice users.
-However, similar presets are often available in the form of default
-settings across most code-based packages, negating the need for the user
-to manually enter each and every choice of setting required for creating
-an image. Most code-based tools also come with documentation, with
-R-packages on the CRAN or **Neuroconductor** repositories having
-compulsory requirements for detailed guidance. Recent packages have even
-started to include documentation in GitHub repositories, or even entire
-papers (cite ggseg and ciftitools) which provide examples of figures
-which can be used as starting points or templates for new users. As the
-popularity of code-sharing for figure increases, there will be a
-cornucopia of templates that can be used as the basis for new figures.
+Being able to exactly replicate your figures via code has marked advantages beyond positive open science practices.
+In particular, the ability to reprogram inputs (such as statistical maps) and settings (such as color schemes, thresholds, and visual orientations) can streamline your entire scientific workflow.
+Changing inputs and settings via code allows for the easy production of multiple figures, such as those resulting from multiple analyses which require similar visualizations.
+A simple for-loop or copying and pasting the code with altered input and/or settings-of-interest can be a powerful method for exploring visualization options or rapidly creating multi-panel figures.
+Likewise, an arduous request from a reviewer or collaborator to alter the image processing or analysis becomes less of a burden when the associated figures can be re-generated with a few lines of code, as opposed to re-pasting and re-illustrating them manually.
+Having a code-base with modifiable inputs can mean that the generation of visualizations requires less time, energy and effort than image and instance specific GUI-based generation.
+This also makes it easier to generate consistent figures across subsequent projects.
+Keep in mind that the gains of writing code for your figures are cumulative, and in addition to improving your programming, you start to build a code-base for figure generation that you can continue to reuse and share throughout your scientific career.
 
-While brain visualizations are often thought of as the end results of
-analyses, they also form a vital part of quality control for imaging
-data. Tools to automatically detect artefacts, de-noise the data and
-generate derivatives are becoming more robust, but we are not yet at the
-stage where visualizing the data during processing is no longer
-necessary. Nonetheless, when working with large datasets such as Human
-Connectome Project (cite) or UK BioBank (cite), it is unfeasible to use
-traditional GUI-based tool to visually check the data. The time it takes
-to open a single file and achieve the desired visualization settings
-vastly compounds when working with large datasets. Knowing how to
-programmatically generate brain visualizations can allow you to iterate
-your visualization code over each image of a large datasets making
-checking the quality of each data processing or analysis step accessible
-and achievable. The visual outputs of each iteration can be complied
-into accessible documents which can be easily scrolled, with more
-advanced usage allowing for the creation of interactive HTML reports,
-similar to those created by tools like mriQC (cite). Increasing capacity
-to conduct visual quality control on larger datasets can increase the
-identification of processing errors and result in more reliable and
-valid findings from your data.
+Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations.
+Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users.
+However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image.
+Most code-based tools also come with documentation, with R-packages on the *CRAN* or *Neuroconductor* (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance.
+Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, & Mejia, 2022; Mowinckel & Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer & Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users.
+As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.
 
-### Integrative and Interactive reporting
+While brain visualizations are often thought of as the end results of analyses, they also form a vital part of quality control for imaging data.
+Tools to automatically detect artefacts, de-noise the data and generate derivatives are becoming more robust, but we are not yet at the stage where visualizing the data during processing is no longer necessary.
+Nonetheless, when working with large datasets such as Human Connectome Project (Van Essen et al., 2013) or UK BioBank (Sudlow et al., 2015), it is unfeasible to use traditional GUI-based tool to visually examine the data.
+The time it takes to open a single file and achieve the desired visualization settings vastly compounds when working with large datasets.
+Knowing how to programmatically generate brain visualizations can allow you to iterate your visualization code over each image of a large datasets making checking the quality of each data processing or analysis step accessible and achievable.
+The visual outputs of each iteration can be complied into accessible documents which can be easily scrolled, with more advanced usage allowing for the creation of interactive HTML reports, similar to those created by standardized data processing tools like *fmriprep* (Esteban et al., 2019).
+Increasing capacity to conduct visual quality control on larger datasets can increase the identification of processing errors and result in more reliable and valid findings from your data.
 
-Often programming languages such as R, Python and MATLAB are used for
-the analysis and non-brain visualizations in neuroimaging studies, but
-the brain visualizations resulting from these analyses are outsourced to
-separate GIU-based visualization tools such as FSLeyes, Freeview or
-ITK-snap. Switching from your analysis environment to a GUI-based
-visualization process be a cumbersome deviation from the scientific
-workflow. This can make debugging errors more difficult, as you have to
-regularly switch program to visually examine the results of any
-modifications or adjustments to prior analyses. Using the brain
-visualization tools that already exist within your chosen programming
-environment can provide instant visual feedback on the impact of
-modifications to processing or analyses.
+# Integrative and Interactive Reporting
 
-Increasingly popular tools such as R-Markdown, Quarto and Jupyter
-Notebook allow for the mixing of prose and code in a single script,
-resulting in fully reproducible and publication ready papers. By using
-code-based tools available within your preferred environment, brain
-visualizations can be directly integrated and embedded within a paper or
-report. Some journals that publish neuroimaging studies are moving
-towards allowing reproducible manuscripts, including reproducible
-figures (cite e-life, f1000,plos), with some even allowing on-demand
-re-running of code using cloud services (cite).
+Often programming languages such as R, Python and MATLAB are used for the analysis and non-brain visualizations in neuroimaging studies, but the brain visualizations resulting from these analyses are outsourced to separate GUI's of tools such as *FSLeyes*, *Freeview* or *ITK-snap*.
+Switching from your analysis environment to a GUI-based visualization process can be a cumbersome deviation from the scientific workflow.
+This can make debugging errors more difficult, as you have to regularly switch program to visually examine the results of any modifications or adjustments to prior analyses.
+Using the brain visualization tools that already exist within your chosen programming environment can provide instant visual feedback on the impact of modifications to processing or analyses.
 
-Neuroimaging data are often spatially 3D and can have multiple time
-points, adding a 4th dimension (e.g., fMRI data). Thus, communicating
-findings or evaluating quality using static 2D slices is challenging,
-and may not be the best representation of the data, or the
-interpretations. While well-curated 3D renderings can help with spatial
-localisation (see madan), in the end, static images can only provide an
-incomplete representation of the data, and forces researchers to choose
-the "best" angle to show, which often involves compromising one result
-to emphasize another. An added advantage of some of the code-based tools
-is that you can generate 'rich' media like interactive widgets --
-figures or animations, which allow users to zoom, rotate and scroll
-through slices. Interacting with a figure in this way can improve
-scientific communication of findings. Linking to or even embedding these
-videos or interactive figures in papers can greatly enhance the
-communication of findings and make your paper more engaging for the
-reader. Such rich brain visualizations lend themselves to being embedded
-or shared on science communication mediums other than academic papers -
-such as presentations, websites and social media - all of which can
-promote the communication of your research with peers and a reach larger
-audiences. This last point is becoming increasingly saliet, as marketing
-science on social media has become a core medium for the spreading
-discoveries, science communication and even a primary avenue for
-obtaining employment for early-career re (Cite?). Overall, public
-engagement, whether it is a researcher, a member of a jury or civil
-society, is one of the keystones of science, and the images we create
-are at the center of the process (Li and Xie, 2020:
-10.1177/0022243719881113).
+Increasingly popular software such as *R Markdown*, *Quarto* and *Jupyter Notebook* allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers.
+By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report.
+For instance, a fully reproducible version of the current paper can be found on [GitHub](https://github.com/sidchop/Brain_comms_field_potential).
+Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.
+*e-Life*, *Aperture Neuro*), with other journals like *F1000Research* and *GigaScience* even allowing on-demand re-running of code computational environment linked to the associated article using 'compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),
 
-### Examples of neuroimaging visualization packages available in R
+Neuroimaging data are often spatially 3D and can have multiple time points, adding a 4th dimension (e.g., fMRI data).
+Thus, communicating findings or evaluating quality using static 2D slices is challenging, and may not be the best representation of the data, or the interpretations.
+While well-curated 3D renderings can help with spatial localisation (see Madan, 2015; Pernet & Madan, 2019), in the end, static images can only provide an incomplete representation of the data, and forces researchers to choose the "best" angle or slice to show, which often involves compromising one result to emphasize another.
+An added advantage of some of the code-based tools is that you can generate 'rich' media like interactive widgets -- figures or animations, which allow users to zoom, rotate and scroll through slices.
+Interacting with a figure in this way can improve scientific communication of findings.
+Linking to or even embedding these videos or interactive figures in papers can greatly enhance the communication of findings and make your paper more engaging for the reader.
+Such rich brain visualizations lend themselves to being embedded or shared on science communication mediums other than academic papers - such as presentations, websites and social media - all of which can promote the communication of your research with peers and a reach larger audiences (Li and Xie, 2020).
+This last point is becoming increasingly salient as marketing science on social media has become a core medium for spreading discoveries, science communication to the public, and even a primary avenue for employment opportunities for early-career researchers (Baker, 2015; Lee, 2019).
+Overall, public engagement is one of the cornerstones of science, and the images we create are at the center of the process.
 
-The following four sections provide brief examples packages and
-functions available in R for visualizing voxel, vertex, ROI and
-edge-level data. A didactic introduction to these tools is provided in a
-accompanying [collection of beginner friendly
-R-Notebooks](ttps://github.com/sidchop/neuRo-vis-BrainHack-2021). This
-is not an exhaustive list of packages available for visualizing brain
-data in R, rather, the following sections and accompanying notebooks aim
-to give the reader a sense of the available options.
+\
+
+|                                 | Voxel | Vertex | ROI | Edge | Streamlines |
+|:--------------------------------|:-----:|:------:|:---:|:----:|:-----------:|
+| R                               |       |        |     |      |             |
+| ciftitools                      |   ✓   |   ✓    | ✓\* |      |             |
+| fsbrain                         |   ✓   |   ✓    | ✓\* |      |             |
+| oro.nifti                       |   ✓   |        |     |      |             |
+| neurobase                       |   ✓   |        |     |      |             |
+| ggseg                           |       |        |  ✓  |      |             |
+| brainconn                       |       |        |     |  ✓   |             |
+| Python                          |       |        |     |      |             |
+| surfice                         |   ✓   |   ✓    |  ✓  |  ✓   |      ✓      |
+| nilearn                         |   ✓   |   ✓    |  ✓  |  ✓   |             |
+| Visbrain                        |   ✓   |   ✓    |  ✓  |  ✓   |             |
+| Pycortex                        |   ✓   |   ✓    | ✓\* |      |             |
+| pySurfer                        |       |   ✓    | ✓\* |      |             |
+| Brainspace/surfplot             |       |   ✓    | ✓\* |      |             |
+| netneurotools                   |       |   ✓    | ✓\* |      |             |
+| Brainplotlib                    |       |   ✓    | ✓\* |      |             |
+| DIPY                            |   ✓   |        |     |      |      ✓      |
+| mrivis                          |   ✓   |        |     |      |             |
+| ENIGMA toolbox                  |       |        |  ✓  |      |             |
+| ggseg                           |       |        |  ✓  |      |             |
+| graphpype                       |       |        |     |  ✓   |             |
+| MATLAB                          |       |        |     |      |             |
+| Vistasoft                       |   ✓   |   ✓    |  ✓  |      |      ✓      |
+| BrainNetViewer                  |   ✓   |        |  ✓  |  ✓   |             |
+| mrtools                         |   ✓   |   ✓    | ✓\* |      |             |
+| FieldTrip                       |   ✓   |   ✓    |     |      |             |
+| ECoG/fMRI visualization toolbox |       |   ✓    | ✓\* |      |             |
+| plotSurfaceROIBoundary          |       |   ✓    | ✓\* |      |             |
+| Brainspace                      |       |   ✓    | ✓\* |      |             |
+| CandlabCore                     |   ✓   |        |  ✓  |      |             |
+| ENIGMA toolbox                  |       |        |  ✓  |      |             |
+
+\
+
+# Examples of neuroimaging visualization packages available in R
+
+The following four sections provide brief examples packages and functions available in R for visualizing voxel, vertex, ROI and edge-level data.
+A didactic introduction to these tools is provided in a accompanying [collection of beginner friendly R-Notebooks](https://github.com/sidchop/neuRo-vis-BrainHack-2021).
+This is not an exhaustive list of packages available for visualizing brain data in R, rather, the following sections and accompanying notebooks aim to give the reader a sense of the available options.
 
@@
 ```
-```{r Figure1 , echo=FALSE, out.height = '80%', out.width = '140%'}
+```{r Figure1 , echo=FALSE, out.height = '80%', out.width = '80%', fig.align='center'}
+
 library(patchwork)
@@
 for (f in 1:length(fig_name)) { 
+  knitr::plot_crop(paste0('data/',fig_name[f],'.png'))
   figs[[f]] <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/',fig_name[f],'.png')),
@@
 
-patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[4]]|(figs[[3]]/figs[[10]]/figs[[11]])
-
-#& theme(text = element_text('Times New Roman'))
+patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]|(figs[[3]]/figs[[4]]/figs[[10]])
 
 patchwork + plot_annotation(tag_levels = 'A',
-                            title = 'Examples of brain visualizations in R')
+                            title = 'Examples of brain visualizations in R') &
+    theme(plot.tag = element_text(face = 'bold'),
+          plot.title = element_text(face="bold"))
 
@@
 
-\
-*Figure 1. Examples of brain imaging visualization make in using
-different R-packages.* A) Voxel-based statistical map threshold and
-overlaid over a T1-weighted template data, with a single axial slice
-shown. Made using the the `ortho2` function from the `neurobase`
-package. B) A voxel-level cortical parcellation overlaid on T1-weighted
-MRI data shown in 9-slice axial orientation. Made using the `overlay`
-function from the `neurobase` package. C) A CIFTI format surface atlas
-with a corresponding statistic assigned to each regions, with both
-hemispheres displayed on a inflated template surface in lateral view.
-Made using the `view_xifti_surface` from the `ciftiTools` package. D) A
-coronal cross-sectional rendering of X, where a statisitcal alue has
-been assigned to each of the X regions.
+*Figure 1.
+Examples of brain imaging visualization make in using different R-packages.* A) Voxel-based statistical map threshold and overlaid over a T1-weighted template data, with a single axial slice shown.
+Made using the the `ortho2` function from the `neurobase` package.
+B) A voxel-level cortical parcellation overlaid on T1-weighted MRI data shown in 9-slice axial orientation.
+Made using the `overlay` function from the `neurobase` package.
+C) A CIFTI format surface ROI atlas with a corresponding statistic assigned to each regions, with both hemispheres displayed on a inflated template surface in lateral view.
+Made using the `view_xifti_surface` from the `ciftiTools` package.
+D) A coronal cross-sectional rendering of subcortical structures where a statistical value has been assigned to each region.
+Made using the `aseg` atlas from the `ggseg` package.
+E) A 3D rendering of 9 bilateral subcortical regions where a statistical value has been assigned to each region.
+Made using the `aseg` atlas from the `ggseg3d` package.
+F) Medial and lateral views of a ROI atlas displayed on inflated template cortical surface where a statistical value has been assigned to each region.
+Made using the `glasser` atlas from the `ggsegGlasser` package, which was plotted using `ggseg`.
+G) Lateral view of a CIFTI format vertex-level data displayed on a inflated template surface.
+Made using the `view_xifti_surface` function from the `ciftiTools` package.
+H) Medial and lateral views of vertex-level data displsayed on a individuals white matter surface.
+Made using the `vis.subject.morph.standard` function from the `fsbrain` package.
+I) A weighted and undirected graph plotted on top, left and front views of a template of a brain rendering.
+Made using the `brainconn` function from the `brainconn` package.
+All code used to complile this figure, as well as the contents of each panel are provided in the Supplement.
 
@@
 
-##### Voxel-level visualizations.
+## Voxel-level visualizations.
 
-The `oro.nifti` package allows for the reading, writing, manipulation
-and visualization of voxel-level imaging data of either nifti, analyze
-or afni formats. In particular, the `image`, `slice` and `orthographic`
-functions allow users to display the desired number of slices in the
-desired orientations, while also providing precise control over overlaid
-images, colour scales, legend placement and other aesthetic settings
-(Fig 1A-B). Smoothing and re-sampling of images is sometimes required
-for visualization purposes, which can be achieved via the `ANTsR`
-/`extrantsr` or `fslr` packages.
+The `oro.nifti` and `neurobase` packages allow for the reading, writing, manipulation and visualization of voxel-level imaging data of either *nifti*, *analyze* or *afni* formats.
+In particular, the `image`, `slice` and `ortho2` functions allow users to display the desired number of slices in the desired orientations, while also providing precise control over overlaid images, color scales, legend placement and other aesthetic settings (Fig 1A-B).
+Smoothing and re-sampling of images is sometimes required for visualization purposes, which can be achieved via the `ANTsR` or `fslr` packages.
 
-##### Vertex-level visualizations.
+## Vertex-level visualizations.
 
-The recently developed `fsbrain` package allows for the visualization of
-vertex-level and atlas-level data which is derieved using FreeSurfer
-formats. It contains many flexible functions for visualising
-individual-level and group-level measures such as cortical thickness,
-volume or surface area (Fig 1E). The package also comes with extensive
-guides and documentations to assist users (cite).
+The recently developed `fsbrain` package allows for the visualization of vertex-level and cortical ROI-level data which were derived using *FreeSurfer*.
+The package contains many flexible functions for visualizing individual-level and group-level measures such as cortical thickness, volume or surface area (Fig 1F).
+In addition to producing publication-ready figures, the visualization functions can allow for visual quality control of large datasets processed using FreeSurfer.
+The package also comes with extensive guides and documentations to assist users (Schäfer & Ecker, 2020).
 
-CIFTI or 'grey-ordinate' data is becoming a popular format for
-structural and functional imaging data, as it combines vertex-level data
-of the cortex with voxel-level data for the cerebellum and sub-cortex.
-In R, CIFTI data can now be read, visualised and manipulated using the
-well-documented `ciftiTools` package (Fig 1C-D,F; cite).
+CIFTI or 'grey-ordinate' data is becoming a popular format for structural and functional imaging data, as it combines vertex-level data of the cortex with voxel-level data for the cerebellum and sub-cortex.
+In R, CIFTI data can now be read, visualized and manipulated using the well-documented `ciftiTools` package (Fig 1C,1G; Pham, Muschelli, & Mejia, 2022).
+This package allows for both vertex-level visualization of the surface as well as voxel-level visualization of cerebellum and subcortex.
 
-##### ROI-level visualizations.
+## ROI-level visualizations.
 
-Statistical parameters can be mapped onto discreet cortical and
-sub-cortical regions using the `ggseg` and `ggseg3d` package. These
-packages flexibly generates aesthetic renderings of cortical,
-sub-cortical and white matter ROIs in 2D and 3D (Fig 1D). Usually,
-ROI-level interpretations are dependent on a standardised atlas or
-parcellation schemes the brain, accordingly this package and its add-ons
-(`ggExtra`) provides a large array of commonly used atlases and some
-functionality for users to contribute other atlases. Additionally, being
-part of the 'Grammar of Graphics' frame work allows for integration with
-packages such as `gganimate`, enabling users to animate and visualise
-dynamic changes in spatial and temporal statistics across ROIs.
+Statistical parameters can be mapped onto discreet cortical and sub-cortical regions using the `ggseg` and `ggseg3d` packages (Mowinckel & Vidal-Piñeiro, 2020).
+These packages flexibly generates aesthetic renderings of cortical, sub-cortical and white matter ROIs in 2D (Fig 1D,1F) and 3D (Fig 1E).
+Usually, ROI-level interpretations are dependent on a standardized atlas or parcellation scheme of the brain and accordingly, this package and its sister-packages (`ggsegExtra`) provide a large array of commonly used atlases and some functionality for users to contribute other atlases.
+Additionally, being part of the 'Grammar of Graphics' framework (Wickham, 2016) allows for integration with packages such as `gganimate`, enabling users to animate and visualize dynamic changes in spatial and temporal statistics across ROIs.
+Notably, the `ciftiTools` package also provides functions to visualize surface and voxel-level ROIs for the cortex and sub-cortex respectively (Fig 1E), flexibly allowing CIFTI format atlases and ROIs to be displayed.
 
-The `ciftiTools` package also allows for surface and voxel-level
-visualization of ROIs for the cortex and sub-cortex respectively (Fig
-1E). Flexibly allowing CIFTI format atlases and ROIs to be displayed.
+## Edge-level visualizations.
 
-##### Edge-level visualizations.
+Analyses which divide the brain into discrete regions and examine pair-wise dependencies between regional phenotypes are becoming increasingly common.
+Often the results of these dependency analyses are statistics relating to 'edges' or links between any two regions.
+The package `brainconn` allows users to plot brain regions as nodes of a network graph, and dependencies between regions as edges of that graph, following a standardized coordinate space in both 2D and interactive 3D (Figure 1I).
+The graphs can be weighted, with the strength of the edges represented with color or line thickness, as well as directed, where arrows will be used in place of edges.
+This package comes with node coordinates corresponding to multiple commonly used atlases and contains functionality for users to easily enter their own custom atlas coordinates.
 
-Analyses which divide the brain into discrete regions and examine
-pair-wise dependences between regional phenotypes are becoming
-increasingly common. Often the results of these dependency analyses are
-statistics relating to 'edges' or links between any two regions. The
-package `brainconn` allows users to plot brain regions as nodes of a
-network graph, and dependences between regions as edges of that graph,
-in both 2D and interactive 3D (Figure 1D). Similar to `ggseg`, this
-package comes within multiple commonly used atlases and contains
-functionality for users to enter their own atlas schemes.
+# Limitations and functionality gaps
 
-### Limitations and functionality gaps in R-packages for brain visualization
+Most of the tools introduced above do not require a strong knowledge of programming, but there is still a steeper learning curve when compared to use a GUI.
+This is especially true when learning how to make fine adjustments to visual auxiliary such as legend placement, font size and multi-panel figure positioning, for the purpose of a publication-ready figure.
+While most code-based tools offer some control over these finer steps, there are differences between them in feature availability and usability.
+Relatedly,while some interactive image viewers which can be opened within integrated development environment (Muschelli, 2016), for quick and interactive viewing of single images, GUI tool can be faster and more practical.
 
-Most of these tools introduced above do not require a strong
-knowledge of programming, but there is still a steeper learning curve
-when compared to GUI-based tools. This is especially true when learning
-to making fine adjustments to visual auxiliary such as legend placement,
-font size and multi-panel figure positioning, for the purpose of a publication
-ready figure. While most tools offer some control over these finer
-steps, there are differences between them in feature availability and
-usability. Although some interactive widgets with limited functionality 
-exist (cite papyr), for quick and interactive viewing of single images, 
-sometimes GUI tool scan be faster and for convenience, can sometimes be 
-opened directly from within some programming environments.
+Often cerebellar and brain-stem regions are not well represented in software (e.g.
+Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes).
+Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
+Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.
 
-[surface projections]
+# References
 
-Some data types are still not well represented in code-based tools. In 
-particular, visualizing streamlines resulting from DWI-based, although 
-some progress is being made (see XXX? - dont know). Similarly, visualizing 
-custom ROIs as 3D renderings, such as those resuting from voxels within 
-subcortex or brain stem, is not yet straight forwared.
+Poldrack, R.
+A., Baker, C.
+I., Durnez, J., Gorgolewski, K.
+J., Matthews, P.
+M., Munafò, M.
+R., ...
+& Yarkoni, T.
+(2017).
+Scanning the horizon: towards transparent and reproducible neuroimaging research.
+Nature reviews neuroscience, 18(2), 115-126.
+
+Steel, G.
+(2013, September 3).
+Publishing research without data is simply advertising, not science.
+Open Knowledge Foundation.
+<https://blog.okfn.org/2013/09/03/publishing-research-without-data-is-simply-advertising-not-science/>
+
+The Comprehensive R Archive Network. (n.d.). Retrieved April 21, 2022, from <https://cran.r-project.org/>
+
+Muschelli, J., Gherman, A., Fortin, J.
+P., Avants, B., Whitcher, B., Clayden, J.
+D., ...
+& Crainiceanu, C.
+M.
+(2019).
+Neuroconductor: an R platform for medical imaging analysis.
+*Biostatistics*, *20*(2), 218-239.
+
+Pham, D., Muschelli, J., & Mejia, A. (2022). ciftiTools: A package for reading, writing, visualizing, and manipulating CIFTI files in R. *NeuroImage*, 118877.
+
+Mowinckel, A. M., & Vidal-Piñeiro, D. (2020). Visualization of brain statistics with R packages ggseg and ggseg3d. *Advances in Methods and Practices in Psychological Science*, *3*(4), 466-483.
+
+Huntenburg, J., Abraham, A., Loula, J., Liem, F., Dadi, K., & Varoquaux, G. (2017). Loading and plotting of cortical surface representations in Nilearn. *Research Ideas and Outcomes*, *3*, e12342.
+
+Wickham H. (2016). *ggplot2: Elegant Graphics for Data Analysis.* Springer-Verlag New York. ISBN 978-3-319-24277-4, <https://ggplot2.tidyverse.org>.
+
+Muschelli, J. (2016). *papayar*. GitHub repository. <https://github.com/muschellij2/papayar>
+
+David C.
+Van Essen, Stephen M.
+Smith, Deanna M.
+Barch, Timothy E.J.
+Behrens, Essa Yacoub, Kamil Ugurbil, for the WU-Minn HCP Consortium.
+(2013).
+The WU-Minn Human Connectome Project: An overview.
+NeuroImage 80(2013):62-79.
+
+Sudlow, C., Gallacher, J., Allen, N., Beral, V., Burton, P., Danesh, J., ...
+& Collins, R.
+(2015).
+UK biobank: an open access resource for identifying the causes of a wide range of complex diseases of middle and old age.
+PLoS medicine, 12(3), e1001779.
+
+Esteban, O., Markiewicz, C.
+J., Blair, R.
+W., Moodie, C.
+A., Isik, A.
+I., Erramuzpe, A., ...
+& Gorgolewski, K.
+J.
+(2019).
+fMRIPrep: a robust preprocessing pipeline for functional MRI.
+Nature methods, 16(1), 111-116.
+
+Pernet, C., & Madan, C. R. (2019). Data visualization for inference in tomographic brain imaging.
+
+Code Ocean. (2021, October 27). Computational Research Platform on. Retrieved April 21, 2022, from <https://codeocean.com/>
+
+Madan, C. R. (2015). Creating 3D visualizations of MRI data: A brief guide. F1000Research, 4.
+
+Baker M. (2015). Social media: A network boost. Nature 518: 263--265. 10.1038/nj7538-263a
+
+Lee J.-S. (2019). How to use Twitter to further your research career. Nature. 10.1038/d41586-019-00535-w
+
+Li, Y., & Xie, Y. (2020). Is a picture worth a thousand words? An empirical study of image content and social media engagement. Journal of Marketing Research, 57(1), 1-19.
+
+Schäfer, T., & Ecker, C. (2020). fsbrain: an R package for the visualization of structural neuroimaging data. bioRxiv.
+
+Chin, R., Chang, S. W., & Holmes, A. J. (2022). Beyond cortex: The evolution of the human brain. *Psychological Review*.
 
 ### Supplement (Code used to generate figure)
+
+\singlespacing
+
+```{r Figure1-sup , echo=FALSE, out.height = '80%', out.width = '80%', fig.align='center', eval=FALSE}
+
+library(patchwork)
+library(ggplot2)
+
+fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1g3','fig1h', 'fig1i')
+figs <- list()
+
+for (f in 1:length(fig_name)) { 
+  knitr::plot_crop(paste0('data/',fig_name[f],'.png'))
+  figs[[f]] <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/',fig_name[f],'.png')),
+                                                             width=ggplot2::unit(1,"npc"),
+                                                             height=ggplot2::unit(1,"npc")))
+}
+
+patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]|(figs[[3]]/figs[[4]]/figs[[10]])
+
+patchwork + plot_annotation(tag_levels = 'A',
+                            title = 'Examples of brain visualizations in R') &
+    theme(plot.tag = element_text(face = 'bold'),
+          plot.title = element_text(face="bold"))
+
+```
 
@@
 #Figure 1e 
-suppressPackageStartupMessages(library(ciftiTools))
+library(ciftiTools)
 parc <- load_parc("Yeo_7")
@@
                 size=.2,
-                show.legend = F,
-                plot.background = "white") + scale_fill_viridis_b()
+                show.legend = T,
+                plot.background = "white") +
+  scale_fill_viridis_b() + 
+   theme_void() +
+    theme(legend.position = "bottom")
 

### 2022-04-21 manuscript.tex
manuscript updated

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{Reproducible and programmatic generation of neuroimaging visualizations}

\author{
    Sidhant Chopra
    \thanks{Corresponding author}
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{\href{mailto:sidhant.chopra@yale.com}{\nolinkurl{sidhant.chopra@yale.com}}} \\
   \And
    Loïc Labache
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Edwina R Orchard
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Avram Holmes
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
  }

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{setspace}\doublespacing
\begin{document}
\maketitle

\begin{abstract}
Add words here.
\end{abstract}

\keywords{
    Brain Visualization
   \and
    MRI Visualization
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The visualization of neuroimaging data is one of the primary ways in which we evaluate data quality, interpret results, and communicate findings. These visualizations are commonly produced using graphic interface-based (GUI) tools where individual images are opened and, within each instance, display settings are manually changed until the desired output is reached. In large part, the choice to use GUI-based software has been driven by a perception of convenience, flexibility, and accessibility. However, there now exists many code-based software packages which are well-documented and do not often require high-level knowledge of programming, making them more accessible to the neuroimaging community (Table 1). These tools are flexible and allow for the generation of reproducible, high-quality, and publication-ready brain visualizations in only a few lines of code (Figure 1), especially within the R, Python and MATLAB environments.

This article will cover three major advantages of using code-generated visualizations over GUI based tools: replicability, flexibility, and integration. First, by generating visualizations using code, you increase the replicability of your figures for yourself, your collaborators and your readers. Second, code-based tools provides more precise controls over display settings, while also benefiting from advantages of programming, such as being able to iteratively and rapidly generate multiple figures. Finally, being able to integrate figure generation into your analysis scripts reduces chances of errors and increases the accessibility of resulting analyses pipeline, with more advanced tools now allowing for the seamless integration of prose and code. Here, we review the advantages of learning and using programmatic neuroimaging visualizations, focusing on benefits to replicability, flexibility and integration. We conclude by introducing examples of R-packages which allow for visualization of statistics at region-of-interest (ROI), voxel, vertex, and edge level data, followed by a brief discussion of limitations and functionality gaps in code-based brain visualization tools.

\hypertarget{replicability}{%
\section{Replicability}\label{replicability}}

In recent years, there have been multiple large-scale efforts empirically demonstrating the lack of reproducibility of findings from neuroimaging data (Poldrack et al., 2017). One common solution proposed for achieving robust and reliable discoveries has been to encourage scientific output which can be transparently evaluated and independently replicated. In practice, this typically entails openly sharing detailed methods, materials, code, and data. While there is a trend towards increasing transparency and code sharing in neuroimaging research, the sharing of code used to generate figures which include brain renderings and spatial maps has been relatively neglected. This gap in reproducibility is partly driven by the fact that brain figures are often created using a manual process that involves tinkering with sliders, buttons, and overlays on a GUI, concluding with a screenshot and sometimes beautification in image processing software like Illustrator or Photoshop. Such a process inherently makes neuroimaging visualizations difficult, if not impossible to replicate, even by the authors themselves.

Visualization scripts should reflect a core feature of open science. Given that brain figures regularly form the centerpiece of interpretation within papers, conference presentations, or news reports, making sure they can be reliably regenerated is crucial for knowledge generation. By writing and sharing code used to generate brain visualizations, a direct and traceable link is established between the underlying data and the corresponding scientific figure. While the code that produces a replicable figure doesn't necessarily reflect the validity of the scientific finding or the accuracy of the associated content, it allows for reproducibility, instilling transparency and robustness, while demonstrating a desire to further scientific knowledge. Some even consider publishing figures which cannot be replicated as closer to advertising, rather than science (Steel, 2013).

While some GUI-based tools have historically offered command-line access to generate replicable visualizations, they can lack both the flexibility to easily generate publication ready figures and the benefits, such as iteration, provided by your preferred programming environment. Likewise, other GUI-based tools offer replicability in the form of automatically generated batch scripts or in-built terminals, which are often idiosyncratic and lack documentation to make them easily usable or reproducible by those not familiar with the specific software.

\hypertarget{flexibility}{%
\section{Flexibility}\label{flexibility}}

Being able to exactly replicate your figures via code has marked advantages beyond positive open science practices. In particular, the ability to reprogram inputs (such as statistical maps) and settings (such as color schemes, thresholds, and visual orientations) can streamline your entire scientific workflow. Changing inputs and settings via code allows for the easy production of multiple figures, such as those resulting from multiple analyses which require similar visualizations. A simple for-loop or copying and pasting the code with altered input and/or settings-of-interest can be a powerful method for exploring visualization options or rapidly creating multi-panel figures. Likewise, an arduous request from a reviewer or collaborator to alter the image processing or analysis becomes less of a burden when the associated figures can be re-generated with a few lines of code, as opposed to re-pasting and re-illustrating them manually. Having a code-base with modifiable inputs can mean that the generation of visualizations requires less time, energy and effort than image and instance specific GUI-based generation. This also makes it easier to generate consistent figures across subsequent projects. Keep in mind that the gains of writing code for your figures are cumulative, and in addition to improving your programming, you start to build a code-base for figure generation that you can continue to reuse and share throughout your scientific career.

Precise controls via code over visualization settings, such as color schemes, legend placement and camera angles, can provide you with much greater flexibility over visualizations. Nonetheless, part of the appeal of GUI-based tools is that the presets for such settings can provide a useful starting point and reduce the decision burden on novice users. However, similar presets are often available in the form of default settings across most code-based packages, negating the need for the user to manually enter each and every choice of setting required for creating an image. Most code-based tools also come with documentation, with R-packages on the \emph{CRAN} or \emph{Neuroconductor} (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance. Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, \& Mejia, 2022; Mowinckel \& Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer \& Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users. As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.

While brain visualizations are often thought of as the end results of analyses, they also form a vital part of quality control for imaging data. Tools to automatically detect artefacts, de-noise the data and generate derivatives are becoming more robust, but we are not yet at the stage where visualizing the data during processing is no longer necessary. Nonetheless, when working with large datasets such as Human Connectome Project (Van Essen et al., 2013) or UK BioBank (Sudlow et al., 2015), it is unfeasible to use traditional GUI-based tool to visually examine the data. The time it takes to open a single file and achieve the desired visualization settings vastly compounds when working with large datasets. Knowing how to programmatically generate brain visualizations can allow you to iterate your visualization code over each image of a large datasets making checking the quality of each data processing or analysis step accessible and achievable. The visual outputs of each iteration can be complied into accessible documents which can be easily scrolled, with more advanced usage allowing for the creation of interactive HTML reports, similar to those created by standardized data processing tools like \emph{fmriprep} (Esteban et al., 2019). Increasing capacity to conduct visual quality control on larger datasets can increase the identification of processing errors and result in more reliable and valid findings from your data.

\hypertarget{integrative-and-interactive-reporting}{%
\section{Integrative and Interactive Reporting}\label{integrative-and-interactive-reporting}}

Often programming languages such as R, Python and MATLAB are used for the analysis and non-brain visualizations in neuroimaging studies, but the brain visualizations resulting from these analyses are outsourced to separate GUI's of tools such as \emph{FSLeyes}, \emph{Freeview} or \emph{ITK-snap}. Switching from your analysis environment to a GUI-based visualization process can be a cumbersome deviation from the scientific workflow. This can make debugging errors more difficult, as you have to regularly switch program to visually examine the results of any modifications or adjustments to prior analyses. Using the brain visualization tools that already exist within your chosen programming environment can provide instant visual feedback on the impact of modifications to processing or analyses.

Increasingly popular software such as \emph{R Markdown}, \emph{Quarto} and \emph{Jupyter Notebook} allow for the mixing of prose and code in a single script, resulting in fully reproducible and publication ready papers. By using code-based tools available within your preferred environment, brain visualizations can be directly integrated and embedded within a paper or report. For instance, a fully reproducible version of the current paper can be found on \href{https://github.com/sidchop/Brain_comms_field_potential}{GitHub}. Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.~\emph{e-Life}, \emph{Aperture Neuro}), with other journals like \emph{F1000Research} and \emph{GigaScience} even allowing on-demand re-running of code computational environment linked to the associated article using `compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),

Neuroimaging data are often spatially 3D and can have multiple time points, adding a 4th dimension (e.g., fMRI data). Thus, communicating findings or evaluating quality using static 2D slices is challenging, and may not be the best representation of the data, or the interpretations. While well-curated 3D renderings can help with spatial localisation (see Madan, 2015; Pernet \& Madan, 2019), in the end, static images can only provide an incomplete representation of the data, and forces researchers to choose the ``best'' angle or slice to show, which often involves compromising one result to emphasize another. An added advantage of some of the code-based tools is that you can generate `rich' media like interactive widgets -- figures or animations, which allow users to zoom, rotate and scroll through slices. Interacting with a figure in this way can improve scientific communication of findings. Linking to or even embedding these videos or interactive figures in papers can greatly enhance the communication of findings and make your paper more engaging for the reader. Such rich brain visualizations lend themselves to being embedded or shared on science communication mediums other than academic papers - such as presentations, websites and social media - all of which can promote the communication of your research with peers and a reach larger audiences (Li and Xie, 2020). This last point is becoming increasingly salient as marketing science on social media has become a core medium for spreading discoveries, science communication to the public, and even a primary avenue for employment opportunities for early-career researchers (Baker, 2015; Lee, 2019). Overall, public engagement is one of the cornerstones of science, and the images we create are at the center of the process.

\hfill\break

\begin{longtable}[]{@{}lccccc@{}}
\toprule
& Voxel & Vertex & ROI & Edge & Streamlines \\
\midrule
\endhead
R & & & & & \\
ciftitools & ✓ & ✓ & ✓* & & \\
fsbrain & ✓ & ✓ & ✓* & & \\
oro.nifti & ✓ & & & & \\
neurobase & ✓ & & & & \\
ggseg & & & ✓ & & \\
brainconn & & & & ✓ & \\
Python & & & & & \\
surfice & ✓ & ✓ & ✓ & ✓ & ✓ \\
nilearn & ✓ & ✓ & ✓ & ✓ & \\
Visbrain & ✓ & ✓ & ✓ & ✓ & \\
Pycortex & ✓ & ✓ & ✓* & & \\
pySurfer & & ✓ & ✓* & & \\
Brainspace/surfplot & & ✓ & ✓* & & \\
netneurotools & & ✓ & ✓* & & \\
Brainplotlib & & ✓ & ✓* & & \\
DIPY & ✓ & & & & ✓ \\
mrivis & ✓ & & & & \\
ENIGMA toolbox & & & ✓ & & \\
ggseg & & & ✓ & & \\
graphpype & & & & ✓ & \\
MATLAB & & & & & \\
Vistasoft & ✓ & ✓ & ✓ & & ✓ \\
BrainNetViewer & ✓ & & ✓ & ✓ & \\
mrtools & ✓ & ✓ & ✓* & & \\
FieldTrip & ✓ & ✓ & & & \\
ECoG/fMRI visualization toolbox & & ✓ & ✓* & & \\
plotSurfaceROIBoundary & & ✓ & ✓* & & \\
Brainspace & & ✓ & ✓* & & \\
CandlabCore & ✓ & & ✓ & & \\
ENIGMA toolbox & & & ✓ & & \\
\bottomrule
\end{longtable}

\hfill\break

\hypertarget{examples-of-neuroimaging-visualization-packages-available-in-r}{%
\section{Examples of neuroimaging visualization packages available in R}\label{examples-of-neuroimaging-visualization-packages-available-in-r}}

The following four sections provide brief examples packages and functions available in R for visualizing voxel, vertex, ROI and edge-level data. A didactic introduction to these tools is provided in a accompanying \href{https://github.com/sidchop/neuRo-vis-BrainHack-2021}{collection of beginner friendly R-Notebooks}. This is not an exhaustive list of packages available for visualizing brain data in R, rather, the following sections and accompanying notebooks aim to give the reader a sense of the available options.

\newpage
\blandscape

\begin{center}\includegraphics[width=0.8\linewidth,height=0.8\textheight]{manuscript_files/figure-latex/Figure1 -1} \end{center}

\emph{Figure 1. Examples of brain imaging visualization make in using different R-packages.} A) Voxel-based statistical map threshold and overlaid over a T1-weighted template data, with a single axial slice shown. Made using the the \texttt{ortho2} function from the \texttt{neurobase} package. B) A voxel-level cortical parcellation overlaid on T1-weighted MRI data shown in 9-slice axial orientation. Made using the \texttt{overlay} function from the \texttt{neurobase} package. C) A CIFTI format surface ROI atlas with a corresponding statistic assigned to each regions, with both hemispheres displayed on a inflated template surface in lateral view. Made using the \texttt{view\_xifti\_surface} from the \texttt{ciftiTools} package. D) A coronal cross-sectional rendering of subcortical structures where a statistical value has been assigned to each region. Made using the \texttt{aseg} atlas from the \texttt{ggseg} package. E) A 3D rendering of 9 bilateral subcortical regions where a statistical value has been assigned to each region. Made using the \texttt{aseg} atlas from the \texttt{ggseg3d} package. F) Medial and lateral views of a ROI atlas displayed on inflated template cortical surface where a statistical value has been assigned to each region. Made using the \texttt{glasser} atlas from the \texttt{ggsegGlasser} package, which was plotted using \texttt{ggseg}. G) Lateral view of a CIFTI format vertex-level data displayed on a inflated template surface. Made using the \texttt{view\_xifti\_surface} function from the \texttt{ciftiTools} package. H) Medial and lateral views of vertex-level data displsayed on a individuals white matter surface. Made using the \texttt{vis.subject.morph.standard} function from the \texttt{fsbrain} package. I) A weighted and undirected graph plotted on top, left and front views of a template of a brain rendering. Made using the \texttt{brainconn} function from the \texttt{brainconn} package. All code used to complile this figure, as well as the contents of each panel are provided in the Supplement.

\end{landscape}

\hypertarget{voxel-level-visualizations.}{%
\subsection{Voxel-level visualizations.}\label{voxel-level-visualizations.}}

The \texttt{oro.nifti} and \texttt{neurobase} packages allow for the reading, writing, manipulation and visualization of voxel-level imaging data of either \emph{nifti}, \emph{analyze} or \emph{afni} formats. In particular, the \texttt{image}, \texttt{slice} and \texttt{ortho2} functions allow users to display the desired number of slices in the desired orientations, while also providing precise control over overlaid images, color scales, legend placement and other aesthetic settings (Fig 1A-B). Smoothing and re-sampling of images is sometimes required for visualization purposes, which can be achieved via the \texttt{ANTsR} or \texttt{fslr} packages.

\hypertarget{vertex-level-visualizations.}{%
\subsection{Vertex-level visualizations.}\label{vertex-level-visualizations.}}

The recently developed \texttt{fsbrain} package allows for the visualization of vertex-level and cortical ROI-level data which were derived using \emph{FreeSurfer}. The package contains many flexible functions for visualizing individual-level and group-level measures such as cortical thickness, volume or surface area (Fig 1F). In addition to producing publication-ready figures, the visualization functions can allow for visual quality control of large datasets processed using FreeSurfer. The package also comes with extensive guides and documentations to assist users (Schäfer \& Ecker, 2020).

CIFTI or `grey-ordinate' data is becoming a popular format for structural and functional imaging data, as it combines vertex-level data of the cortex with voxel-level data for the cerebellum and sub-cortex. In R, CIFTI data can now be read, visualized and manipulated using the well-documented \texttt{ciftiTools} package (Fig 1C,1G; Pham, Muschelli, \& Mejia, 2022). This package allows for both vertex-level visualization of the surface as well as voxel-level visualization of cerebellum and subcortex.

\hypertarget{roi-level-visualizations.}{%
\subsection{ROI-level visualizations.}\label{roi-level-visualizations.}}

Statistical parameters can be mapped onto discreet cortical and sub-cortical regions using the \texttt{ggseg} and \texttt{ggseg3d} packages (Mowinckel \& Vidal-Piñeiro, 2020). These packages flexibly generates aesthetic renderings of cortical, sub-cortical and white matter ROIs in 2D (Fig 1D,1F) and 3D (Fig 1E). Usually, ROI-level interpretations are dependent on a standardized atlas or parcellation scheme of the brain and accordingly, this package and its sister-packages (\texttt{ggsegExtra}) provide a large array of commonly used atlases and some functionality for users to contribute other atlases. Additionally, being part of the `Grammar of Graphics' framework (Wickham, 2016) allows for integration with packages such as \texttt{gganimate}, enabling users to animate and visualize dynamic changes in spatial and temporal statistics across ROIs. Notably, the \texttt{ciftiTools} package also provides functions to visualize surface and voxel-level ROIs for the cortex and sub-cortex respectively (Fig 1E), flexibly allowing CIFTI format atlases and ROIs to be displayed.

\hypertarget{edge-level-visualizations.}{%
\subsection{Edge-level visualizations.}\label{edge-level-visualizations.}}

Analyses which divide the brain into discrete regions and examine pair-wise dependencies between regional phenotypes are becoming increasingly common. Often the results of these dependency analyses are statistics relating to `edges' or links between any two regions. The package \texttt{brainconn} allows users to plot brain regions as nodes of a network graph, and dependencies between regions as edges of that graph, following a standardized coordinate space in both 2D and interactive 3D (Figure 1I). The graphs can be weighted, with the strength of the edges represented with color or line thickness, as well as directed, where arrows will be used in place of edges. This package comes with node coordinates corresponding to multiple commonly used atlases and contains functionality for users to easily enter their own custom atlas coordinates.

\hypertarget{limitations-and-functionality-gaps}{%
\section{Limitations and functionality gaps}\label{limitations-and-functionality-gaps}}

Most of the tools introduced above do not require a strong knowledge of programming, but there is still a steeper learning curve when compared to use a GUI. This is especially true when learning how to make fine adjustments to visual auxiliary such as legend placement, font size and multi-panel figure positioning, for the purpose of a publication-ready figure. While most code-based tools offer some control over these finer steps, there are differences between them in feature availability and usability. Relatedly,while some interactive image viewers which can be opened within integrated development environment (Muschelli, 2016), for quick and interactive viewing of single images, GUI tool can be faster and more practical.

Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes). Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.

\hypertarget{references}{%
\section{References}\label{references}}

Poldrack, R. A., Baker, C. I., Durnez, J., Gorgolewski, K. J., Matthews, P. M., Munafò, M. R., \ldots{} \& Yarkoni, T. (2017). Scanning the horizon: towards transparent and reproducible neuroimaging research. Nature reviews neuroscience, 18(2), 115-126.

Steel, G. (2013, September 3). Publishing research without data is simply advertising, not science. Open Knowledge Foundation. \url{https://blog.okfn.org/2013/09/03/publishing-research-without-data-is-simply-advertising-not-science/}

The Comprehensive R Archive Network. (n.d.). Retrieved April 21, 2022, from \url{https://cran.r-project.org/}

Muschelli, J., Gherman, A., Fortin, J. P., Avants, B., Whitcher, B., Clayden, J. D., \ldots{} \& Crainiceanu, C. M. (2019). Neuroconductor: an R platform for medical imaging analysis. \emph{Biostatistics}, \emph{20}(2), 218-239.

Pham, D., Muschelli, J., \& Mejia, A. (2022). ciftiTools: A package for reading, writing, visualizing, and manipulating CIFTI files in R. \emph{NeuroImage}, 118877.

Mowinckel, A. M., \& Vidal-Piñeiro, D. (2020). Visualization of brain statistics with R packages ggseg and ggseg3d. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(4), 466-483.

Huntenburg, J., Abraham, A., Loula, J., Liem, F., Dadi, K., \& Varoquaux, G. (2017). Loading and plotting of cortical surface representations in Nilearn. \emph{Research Ideas and Outcomes}, \emph{3}, e12342.

Wickham H. (2016). \emph{ggplot2: Elegant Graphics for Data Analysis.} Springer-Verlag New York. ISBN 978-3-319-24277-4, \url{https://ggplot2.tidyverse.org}.

Muschelli, J. (2016). \emph{papayar}. GitHub repository. \url{https://github.com/muschellij2/papayar}

David C. Van Essen, Stephen M. Smith, Deanna M. Barch, Timothy E.J. Behrens, Essa Yacoub, Kamil Ugurbil, for the WU-Minn HCP Consortium. (2013). The WU-Minn Human Connectome Project: An overview. NeuroImage 80(2013):62-79.

Sudlow, C., Gallacher, J., Allen, N., Beral, V., Burton, P., Danesh, J., \ldots{} \& Collins, R. (2015). UK biobank: an open access resource for identifying the causes of a wide range of complex diseases of middle and old age. PLoS medicine, 12(3), e1001779.

Esteban, O., Markiewicz, C. J., Blair, R. W., Moodie, C. A., Isik, A. I., Erramuzpe, A., \ldots{} \& Gorgolewski, K. J. (2019). fMRIPrep: a robust preprocessing pipeline for functional MRI. Nature methods, 16(1), 111-116.

Pernet, C., \& Madan, C. R. (2019). Data visualization for inference in tomographic brain imaging.

Code Ocean. (2021, October 27). Computational Research Platform on. Retrieved April 21, 2022, from \url{https://codeocean.com/}

Madan, C. R. (2015). Creating 3D visualizations of MRI data: A brief guide. F1000Research, 4.

Baker M. (2015). Social media: A network boost. Nature 518: 263--265. 10.1038/nj7538-263a

Lee J.-S. (2019). How to use Twitter to further your research career. Nature. 10.1038/d41586-019-00535-w

Li, Y., \& Xie, Y. (2020). Is a picture worth a thousand words? An empirical study of image content and social media engagement. Journal of Marketing Research, 57(1), 1-19.

Schäfer, T., \& Ecker, C. (2020). fsbrain: an R package for the visualization of structural neuroimaging data. bioRxiv.

Chin, R., Chang, S. W., \& Holmes, A. J. (2022). Beyond cortex: The evolution of the human brain. \emph{Psychological Review}.

\hypertarget{supplement-code-used-to-generate-figure}{%
\subsubsection{Supplement (Code used to generate figure)}\label{supplement-code-used-to-generate-figure}}

\singlespacing

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#Figure 1A}

\FunctionTok{library}\NormalTok{(neurobase)}
\FunctionTok{library}\NormalTok{(ggplotify)}

\CommentTok{\#Load in a nifti (.nii.gz) file of a standardized template so use as a background. }
\NormalTok{template }\OtherTok{\textless{}{-}} \FunctionTok{readnii}\NormalTok{(}\StringTok{\textquotesingle{}data/MNI152\_T1\_1mm\_brain.nii.gz\textquotesingle{}}\NormalTok{) }\CommentTok{\#load the nifti file into R}

\CommentTok{\#Load in a nifti (.nii.gz) file of the statistic you wanted of overlay, with the same dimensions as the template.  }
\NormalTok{effect }\OtherTok{\textless{}{-}} \FunctionTok{readnii}\NormalTok{(}\StringTok{"data/MNI152\_effect\_size.nii.gz"}\NormalTok{) }

\CommentTok{\#Threshold the statistic map so only values about a specified amount are displayed}
\NormalTok{effect[effect}\SpecialCharTok{\textless{}}\FloatTok{0.3}\NormalTok{] }\OtherTok{\textless{}{-}} \ConstantTok{NA}

\CommentTok{\#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)}
\NormalTok{breaks }\OtherTok{=} \FunctionTok{seq}\NormalTok{(.}\DecValTok{3}\NormalTok{,.}\DecValTok{6}\NormalTok{, }\AttributeTok{by=}\FloatTok{0.005}\NormalTok{)}

\CommentTok{\#[Optional] If you want to output the figure as a .png, open a png image device}
\FunctionTok{png}\NormalTok{(}\StringTok{"data/fig1a.png"}\NormalTok{) }

\CommentTok{\#Use the ortho2 function from the neurobase package to make the figure}
\FunctionTok{ortho2}\NormalTok{(}\AttributeTok{x =}\NormalTok{ template,   }\CommentTok{\#Specify the background template}
       \AttributeTok{y =}\NormalTok{ effect,     }\CommentTok{\#Specify the effect you want to overlay on the tempplate}
       \AttributeTok{crosshairs =}\NormalTok{ F, }\CommentTok{\#Remove the cross{-}hairs}
       \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,   }\CommentTok{\#Make the background white }
       \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the colour scale. In this case I have used the viridis scale from the viridis package. }
       \AttributeTok{xyz =} \FunctionTok{c}\NormalTok{(}\DecValTok{70}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{80}\NormalTok{), }\CommentTok{\#set the x y \& z slice you want to visualise}
       \AttributeTok{useRaster =}\NormalTok{ T,   }\CommentTok{\#Sometimes using Raster makes for clearer plots}
       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{, }\CommentTok{\#Add a colorbar}
       \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
  \FunctionTok{colorbar}\NormalTok{(breaks,}\AttributeTok{col =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{), }
           \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}

\FunctionTok{dev.off}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#Figure 1B}
\CommentTok{\#voxel 2}

\FunctionTok{library}\NormalTok{(neurobase)}
\FunctionTok{library}\NormalTok{(scales)}

\CommentTok{\#Load in a nifti (.nii.gz) file to use as a background. }
\NormalTok{t1 }\OtherTok{\textless{}{-}} \FunctionTok{readnii}\NormalTok{(}\StringTok{\textquotesingle{}data/sub{-}001\_\_t1\_warped.nii.gz\textquotesingle{}}\NormalTok{) }

\NormalTok{atlas }\OtherTok{\textless{}{-}}  \FunctionTok{readnii}\NormalTok{(}\StringTok{\textquotesingle{}data/sub{-}001\_schaefer300n7\_aseg\_to\_dwispace\_gm\_rois.nii.gz\textquotesingle{}}\NormalTok{)}

\FunctionTok{png}\NormalTok{(}\StringTok{\textquotesingle{}data/fig1b.png\textquotesingle{}}\NormalTok{)}
\FunctionTok{overlay}\NormalTok{(}\AttributeTok{x=}\FunctionTok{robust\_window}\NormalTok{(t1), }\AttributeTok{y=}\NormalTok{atlas, }
        \AttributeTok{plot.type =} \StringTok{"single"}\NormalTok{, }
        \AttributeTok{z=}\FunctionTok{c}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{30}\NormalTok{,}\DecValTok{110}\NormalTok{,}\DecValTok{10}\NormalTok{)), }
        \AttributeTok{col.y =}  \FunctionTok{alpha}\NormalTok{(}\FunctionTok{rainbow}\NormalTok{(}\DecValTok{300}\NormalTok{), }\FloatTok{0.3}\NormalTok{),}
        \AttributeTok{plane =} \StringTok{"axial"}\NormalTok{,  }
        \AttributeTok{useRaster =}\NormalTok{ T, }
        \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,}
        \AttributeTok{NA.x=}\NormalTok{T, }
        \AttributeTok{zlim.y =}\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{300}\NormalTok{))}

      \CommentTok{\#  mar = c(0.1, 0.1, 1.5, 0.1)) + \#marget of bottom, left, top, right borders}
\FunctionTok{dev.off}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#vertex 1}
\CommentTok{\#Figure 1B}
\FunctionTok{library}\NormalTok{(rgl)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\CommentTok{\# Load the package and point to the Connectome Workbench}
\FunctionTok{library}\NormalTok{(ciftiTools)}

\FunctionTok{ciftiTools.setOption}\NormalTok{(}\StringTok{"wb\_path"}\NormalTok{, }\StringTok{"/Applications/workbench/"}\NormalTok{)}

\CommentTok{\# Read and visualize a CIFTI file }

\NormalTok{cifti\_fname }\OtherTok{\textless{}{-}}\NormalTok{ ciftiTools}\SpecialCharTok{::}\FunctionTok{ciftiTools.files}\NormalTok{()}\SpecialCharTok{$}\NormalTok{cifti[}\StringTok{"dtseries"}\NormalTok{]}
\NormalTok{surfL\_fname }\OtherTok{\textless{}{-}} \FunctionTok{ciftiTools.files}\NormalTok{()}\SpecialCharTok{$}\NormalTok{surf[}\StringTok{"left"}\NormalTok{]}
\NormalTok{surfR\_fname }\OtherTok{\textless{}{-}} \FunctionTok{ciftiTools.files}\NormalTok{()}\SpecialCharTok{$}\NormalTok{surf[}\StringTok{"right"}\NormalTok{]}

\NormalTok{cii }\OtherTok{\textless{}{-}} \FunctionTok{read\_cifti}\NormalTok{(}
\NormalTok{  cifti\_fname, }\AttributeTok{brainstructures=}\StringTok{"all"}\NormalTok{, }
  \AttributeTok{surfL\_fname=}\NormalTok{surfL\_fname,}
  \AttributeTok{surfR\_fname=}\NormalTok{surfR\_fname)}

\FunctionTok{view\_xifti\_surface}\NormalTok{(cii, }
                   \AttributeTok{hemisphere =} \StringTok{"both"}\NormalTok{, }
                   \AttributeTok{view =} \StringTok{"lateral"}\NormalTok{, }
                   \AttributeTok{idx =} \DecValTok{1}\NormalTok{,}
                   \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{),}
                   \AttributeTok{zlim =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.2}\NormalTok{,}\FloatTok{1.5}\NormalTok{),  }
                   \AttributeTok{legend\_embed =}\NormalTok{ T,}
                   \AttributeTok{cex.title =} \DecValTok{2}\NormalTok{)}

\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1c.png"}\NormalTok{)}
\FunctionTok{rgl.close}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#Vertex 2}
\CommentTok{\#Figure 1X {-} Remove white space}

\FunctionTok{library}\NormalTok{(fsbrain)}

\CommentTok{\#download\_optional\_data()}
\CommentTok{\#download\_fsaverage(accept\_freesurfer\_license = TRUE)}

\NormalTok{subjects\_dir }\OtherTok{\textless{}{-}} \FunctionTok{get\_optional\_data\_filepath}\NormalTok{(}\StringTok{"subjects\_dir"}\NormalTok{)}

\NormalTok{subject\_id }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}subject1\textquotesingle{}}

\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{10000}\NormalTok{))}
\FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}

\NormalTok{cm }\OtherTok{=} \FunctionTok{vis.subject.morph.standard}\NormalTok{(subjects\_dir, }
\NormalTok{                                subject\_id, }\StringTok{\textquotesingle{}sulc\textquotesingle{}}\NormalTok{, }
                                \AttributeTok{fwhm=}\StringTok{\textquotesingle{}10\textquotesingle{}}\NormalTok{, }
                                \AttributeTok{cortex\_only =}\NormalTok{ T, }
                                \AttributeTok{views=}\ConstantTok{NULL}\NormalTok{, }
                                \AttributeTok{makecmap\_options =} \FunctionTok{list}\NormalTok{(}\StringTok{\textquotesingle{}colFn\textquotesingle{}}\OtherTok{=}\NormalTok{colourmap))}
\NormalTok{img }\OtherTok{=} \FunctionTok{export}\NormalTok{(cm, }\AttributeTok{colorbar\_legend=}\StringTok{\textquotesingle{}Effect\textquotesingle{}}\NormalTok{, }\AttributeTok{output\_img =} \StringTok{"data/fig1d.png"}\NormalTok{)}

\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1d.png"}\NormalTok{)}
\FunctionTok{rgl.close}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#ROI1 }
\CommentTok{\#Figure 1e }
\FunctionTok{library}\NormalTok{(ciftiTools)}
\NormalTok{parc }\OtherTok{\textless{}{-}} \FunctionTok{load\_parc}\NormalTok{(}\StringTok{"Yeo\_7"}\NormalTok{)}
\FunctionTok{view\_xifti\_surface}\NormalTok{(parc,  }
                   \AttributeTok{legend\_embed =}\NormalTok{ T,}
                   \AttributeTok{hemisphere =} \StringTok{"right"}\NormalTok{)}

\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1e.png"}\NormalTok{)}

\FunctionTok{rgl.close}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#ROI1 }
\CommentTok{\#Figure 1X {-} combine with previous figure}

\FunctionTok{set.seed}\NormalTok{(}\DecValTok{1993}\NormalTok{) }\CommentTok{\#set a random seed (good practice for reproducibility)}

\NormalTok{parc }\OtherTok{\textless{}{-}} \FunctionTok{load\_parc}\NormalTok{(}\StringTok{"Schaefer\_400"}\NormalTok{)}

\NormalTok{ramdom\_metric }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{400}\NormalTok{)}

\NormalTok{cii }\OtherTok{\textless{}{-}} \FunctionTok{move\_from\_mwall}\NormalTok{(cii, }\ConstantTok{NA}\NormalTok{)}

\NormalTok{parc\_vec }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FunctionTok{as.matrix}\NormalTok{(parc))}

\NormalTok{xii\_metric }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\ConstantTok{NA}\NormalTok{, ramdom\_metric)[parc\_vec }\SpecialCharTok{+} \DecValTok{1}\NormalTok{]}

\NormalTok{xii1 }\OtherTok{\textless{}{-}} \FunctionTok{select\_xifti}\NormalTok{(cii, }\DecValTok{1}\NormalTok{)}

\NormalTok{xii\_metric }\OtherTok{\textless{}{-}} \FunctionTok{newdata\_xifti}\NormalTok{(xii1, xii\_metric)}

\NormalTok{plot2 }\OtherTok{\textless{}{-}} \FunctionTok{view\_xifti\_surface}\NormalTok{(xii\_metric, }
                            \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{400}\NormalTok{), }
                            \AttributeTok{borders =} \StringTok{"black"}\NormalTok{, }
                            \AttributeTok{hemisphere =} \StringTok{"both"}\NormalTok{,}
                            \AttributeTok{view =} \StringTok{\textquotesingle{}lateral\textquotesingle{}}\NormalTok{)}

\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1f.png"}\NormalTok{)}

\FunctionTok{rgl.close}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#ROI2}

\CommentTok{\#devtools::install\_github("LCBC{-}UiO/ggsegGlasser")}
\FunctionTok{library}\NormalTok{(ggseg)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(ggsegGlasser)}

\FunctionTok{set.seed}\NormalTok{(}\DecValTok{1993}\NormalTok{) }\CommentTok{\#set a random seed (good practice for reproducibility)}

\NormalTok{base\_atlas }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{na.omit}\NormalTok{(}\FunctionTok{cbind}\NormalTok{(glasser}\SpecialCharTok{$}\NormalTok{data}\SpecialCharTok{$}\NormalTok{region, glasser}\SpecialCharTok{$}\NormalTok{data}\SpecialCharTok{$}\NormalTok{hemi)))}

\FunctionTok{colnames}\NormalTok{(base\_atlas) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"region"}\NormalTok{, }\StringTok{"hemi"}\NormalTok{)}

\NormalTok{Effect }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\FunctionTok{dim}\NormalTok{(base\_atlas)[}\DecValTok{1}\NormalTok{]) }\CommentTok{\#generate a random numbers for each roi in the atlas}

\NormalTok{base\_atlas }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(Effect, base\_atlas)}

\NormalTok{cortex }\OtherTok{\textless{}{-}} \FunctionTok{ggseg}\NormalTok{(}\AttributeTok{atlas =}\NormalTok{ glasser,}
                \AttributeTok{.data =}\NormalTok{ base\_atlas,}
                \AttributeTok{mapping=}\FunctionTok{aes}\NormalTok{(}\AttributeTok{fill=}\NormalTok{Effect), }
                \AttributeTok{position=}\StringTok{"stacked"}\NormalTok{,}
                \AttributeTok{colour=}\StringTok{"black"}\NormalTok{,}
                \AttributeTok{size=}\NormalTok{.}\DecValTok{2}\NormalTok{,}
                \AttributeTok{show.legend =}\NormalTok{ T,}
                \AttributeTok{plot.background =} \StringTok{"white"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_viridis\_b}\NormalTok{() }\SpecialCharTok{+} 
   \FunctionTok{theme\_void}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}

\NormalTok{sub\_base\_atlas }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{na.omit}\NormalTok{(}\FunctionTok{cbind}\NormalTok{(aseg}\SpecialCharTok{$}\NormalTok{data}\SpecialCharTok{$}\NormalTok{region, aseg}\SpecialCharTok{$}\NormalTok{data}\SpecialCharTok{$}\NormalTok{hemi)))}

\FunctionTok{colnames}\NormalTok{(sub\_base\_atlas) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"region"}\NormalTok{, }\StringTok{"hemi"}\NormalTok{)}

\NormalTok{Effect }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\FunctionTok{dim}\NormalTok{(sub\_base\_atlas)[}\DecValTok{1}\NormalTok{])}

\NormalTok{sub\_base\_atlas }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(Effect, sub\_base\_atlas)}

\NormalTok{subcortex }\OtherTok{\textless{}{-}} \FunctionTok{ggseg}\NormalTok{(}\AttributeTok{atlas =}\NormalTok{ aseg,}
                   \AttributeTok{.data =}\NormalTok{ sub\_base\_atlas,}
                   \AttributeTok{mapping=}\FunctionTok{aes}\NormalTok{(}\AttributeTok{fill=}\NormalTok{Effect), }
                   \AttributeTok{position =} \StringTok{"dispersed"}\NormalTok{,}
                   \AttributeTok{colour=}\StringTok{"black"}\NormalTok{,}
                   \AttributeTok{hemi =}\FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}left\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}right\textquotesingle{}}\NormalTok{),}
                   \AttributeTok{size=}\NormalTok{.}\DecValTok{2}\NormalTok{,}
                   \AttributeTok{show.legend =}\NormalTok{ T, }
                   \AttributeTok{plot.background =} \StringTok{"white"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{scale\_fill\_viridis\_b}\NormalTok{() }

\FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1g1.png\textquotesingle{}}\NormalTok{, }\AttributeTok{plot =}\NormalTok{ cortex, }\AttributeTok{device =} \StringTok{\textquotesingle{}png\textquotesingle{}}\NormalTok{, }\AttributeTok{bg =} \StringTok{\textquotesingle{}white\textquotesingle{}}\NormalTok{)}
\FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1g2.png\textquotesingle{}}\NormalTok{, }\AttributeTok{plot =}\NormalTok{ subcortex, }\AttributeTok{device =} \StringTok{\textquotesingle{}png\textquotesingle{}}\NormalTok{, }\AttributeTok{bg =} \StringTok{\textquotesingle{}white\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{make\_ggseg3d }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(attribute, }
                         \AttributeTok{colour.pal =} \FunctionTok{c}\NormalTok{(}\StringTok{"light yellow"}\NormalTok{,}
                                        \StringTok{"orange"}\NormalTok{,}
                                        \StringTok{"red"}\NormalTok{,}
                                        \StringTok{"dark red"}\NormalTok{), }
                         \AttributeTok{hide.colourbar=}\ConstantTok{FALSE}\NormalTok{, }
                         \AttributeTok{output.png=}\ConstantTok{FALSE}\NormalTok{, }
                         \AttributeTok{file.name=}\StringTok{"ggseg\_3d.png"}\NormalTok{) \{}
  \CommentTok{\# Inputs: }
  \CommentTok{\#\textquotesingle{} attribute = This must be a numeric vector in this: Left{-}Thalamus, Left{-}Caudate, Left{-}Putamen, Left{-}Pallidum Left{-}Hippocampus, Left{-}Amygdala, Left{-}Accumbens{-}area, Right{-}Thalamus{-}Proper, Right{-}Caudate, Right{-}Putamen, Right{-}Pallidum, Right{-}Hippocampus, Right{-}Amygdala, Right{-}Accumbens{-}area}

  \FunctionTok{library}\NormalTok{(ggseg3d)}
  \FunctionTok{library}\NormalTok{(tidyr)}
  \FunctionTok{library}\NormalTok{(dplyr)}
  \CommentTok{\#remove(aseg\_3d)}
\NormalTok{  aseg\_3d }\OtherTok{\textless{}{-}}\NormalTok{ aseg\_3d}
\NormalTok{  aseg\_3d }\OtherTok{\textless{}{-}}\NormalTok{ tidyr}\SpecialCharTok{::}\FunctionTok{unnest}\NormalTok{(aseg\_3d, }\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(ggseg\_3d))}

\NormalTok{  attribute.ggseg3d }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\DecValTok{4}\NormalTok{), attribute[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{], }\FunctionTok{rep}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\DecValTok{3}\NormalTok{), attribute[}\DecValTok{5}\SpecialCharTok{:}\DecValTok{7}\NormalTok{],}
                         \FunctionTok{rep}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\DecValTok{5}\NormalTok{), attribute[}\DecValTok{8}\SpecialCharTok{:}\DecValTok{14}\NormalTok{],  }\FunctionTok{rep}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\DecValTok{6}\NormalTok{))}

\NormalTok{  data }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{mutate}\NormalTok{(aseg\_3d, }\AttributeTok{attribute =}\NormalTok{  attribute.ggseg3d)}
  \CommentTok{\#remove NA regions}
\NormalTok{  aseg\_3d[}\FunctionTok{which}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(data}\SpecialCharTok{$}\NormalTok{attribute)),] }\OtherTok{\textless{}{-}} \ConstantTok{NA}
\NormalTok{  aseg\_3d }\OtherTok{\textless{}{-}}\NormalTok{ tidyr}\SpecialCharTok{::}\FunctionTok{drop\_na}\NormalTok{(aseg\_3d)}

\NormalTok{  data[}\FunctionTok{which}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(data}\SpecialCharTok{$}\NormalTok{attribute)),] }\OtherTok{\textless{}{-}} \ConstantTok{NA}
\NormalTok{  data }\OtherTok{\textless{}{-}}\NormalTok{ tidyr}\SpecialCharTok{::}\FunctionTok{drop\_na}\NormalTok{(data)}
\NormalTok{  data}\SpecialCharTok{$}\NormalTok{attribute[data}\SpecialCharTok{$}\NormalTok{attribute}\SpecialCharTok{==}\DecValTok{0}\NormalTok{]}\OtherTok{\textless{}{-}}\ConstantTok{NA} \CommentTok{\#make 0 valus NA so they are set as grey in ggseg3d}

\NormalTok{  scene}\OtherTok{=}\FunctionTok{list}\NormalTok{(}\AttributeTok{camera =} \FunctionTok{list}\NormalTok{(}\AttributeTok{eye =} \FunctionTok{list}\NormalTok{(}\AttributeTok{x =} \DecValTok{0}\NormalTok{, }\AttributeTok{y =} \DecValTok{1}\NormalTok{, }\AttributeTok{z =} \SpecialCharTok{{-}}\FloatTok{2.25}\NormalTok{)),}
             \AttributeTok{aspectratio =} \FunctionTok{list}\NormalTok{(}\AttributeTok{x=}\FloatTok{1.6}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.6}\NormalTok{,}\AttributeTok{z=}\FloatTok{1.6}\NormalTok{))}

\NormalTok{  plot }\OtherTok{\textless{}{-}}\NormalTok{ ggseg3d}\SpecialCharTok{::}\FunctionTok{ggseg3d}\NormalTok{(}\AttributeTok{.data =}\NormalTok{ data, }
                           \AttributeTok{atlas =}\NormalTok{ aseg\_3d, }
                           \AttributeTok{colour =} \StringTok{"attribute"}\NormalTok{, }
                           \AttributeTok{text =} \StringTok{"attribute"}\NormalTok{,}
                           \AttributeTok{palette =}\NormalTok{ colour.pal)}
\NormalTok{  plot }\OtherTok{\textless{}{-}} \FunctionTok{remove\_axes}\NormalTok{(plot)}
\NormalTok{  plot }\OtherTok{\textless{}{-}}\NormalTok{ plotly}\SpecialCharTok{::}\FunctionTok{layout}\NormalTok{(plot, }
                         \AttributeTok{scene =}\NormalTok{ scene, }
                         \AttributeTok{width =} \DecValTok{600}\NormalTok{, }\AttributeTok{height =} \DecValTok{600}\NormalTok{) }

  \ControlFlowTok{if}\NormalTok{(hide.colourbar}\SpecialCharTok{==}\ConstantTok{TRUE}\NormalTok{)\{}
\NormalTok{    plot }\OtherTok{\textless{}{-}}\NormalTok{ plotly}\SpecialCharTok{::}\FunctionTok{hide\_colorbar}\NormalTok{(plot)}
\NormalTok{  \}}

  \ControlFlowTok{if}\NormalTok{( output.png}\SpecialCharTok{==}\ConstantTok{TRUE}\NormalTok{)\{}
\NormalTok{    plotly}\SpecialCharTok{::}\FunctionTok{orca}\NormalTok{(plot, }\AttributeTok{file =}\NormalTok{  file.name)}
\NormalTok{  \}}

  \FunctionTok{return}\NormalTok{(plot)}

\NormalTok{\}}

\FunctionTok{set.seed}\NormalTok{(}\DecValTok{1993}\NormalTok{)}
\NormalTok{volume }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{20}\NormalTok{, }\DecValTok{14}\NormalTok{) }\CommentTok{\#randomly generated data for 14 structures}
\FunctionTok{make\_ggseg3d}\NormalTok{(volume, }
             \AttributeTok{colour.pal =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(volume)), }
             \AttributeTok{output.png =}\NormalTok{ T, }\AttributeTok{file.name =} \StringTok{"data/fig1g3.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#Edge (also add 3d version)}
\CommentTok{\#Fig1X}

\CommentTok{\#remotes::install\_github("sidchop/brainconn")}
\FunctionTok{library}\NormalTok{(brainconn)}

\NormalTok{conmat }\OtherTok{\textless{}{-}}\NormalTok{ example\_weighted\_undirected}
\NormalTok{degree }\OtherTok{\textless{}{-}} \FunctionTok{rowSums}\NormalTok{(conmat)[}\FunctionTok{which}\NormalTok{(}\FunctionTok{rowSums}\NormalTok{(conmat)}\SpecialCharTok{!=}\DecValTok{0}\NormalTok{)]}
\NormalTok{fig1h }\OtherTok{\textless{}{-}} \FunctionTok{brainconn}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
                   \AttributeTok{conmat=}\NormalTok{conmat, }
                   \AttributeTok{node.size =}\NormalTok{ degree}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
                   \AttributeTok{view=}\StringTok{"ortho"}\NormalTok{, }
                   \AttributeTok{edge.color.weighted =}\NormalTok{ T,}
                   \AttributeTok{background.alpha =} \FloatTok{0.4}\NormalTok{, }
                   \AttributeTok{show.legend =}\NormalTok{ F,}
                   \AttributeTok{edge.color =} \FunctionTok{scale\_edge\_colour\_gradient2}\NormalTok{(}\AttributeTok{low=}\StringTok{\textquotesingle{}yellow\textquotesingle{}}\NormalTok{, }\AttributeTok{mid=}\StringTok{\textquotesingle{}orange\textquotesingle{}}\NormalTok{, }\AttributeTok{high=}\StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{)) }
\FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1h.png\textquotesingle{}}\NormalTok{, }
       \AttributeTok{plot =}\NormalTok{ fig1h, }
       \AttributeTok{device =} \StringTok{\textquotesingle{}png\textquotesingle{}}\NormalTok{,}
       \AttributeTok{bg =} \StringTok{\textquotesingle{}white\textquotesingle{}}\NormalTok{,}
       \AttributeTok{height =} \DecValTok{7}\NormalTok{, }
       \AttributeTok{units =} \StringTok{"in"}\NormalTok{)}

\FunctionTok{brainconn3D}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
            \AttributeTok{conmat=}\NormalTok{conmat,}
            \AttributeTok{show.legend =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\bibliographystyle{unsrt}
\bibliography{}

\end{document}

### 2022-04-23 manuscript.Rmd
test
.

@@
   - name: Loïc Labache
-    department: School of Psychology
-    affiliation: Department of Psychology
+    department: Department of Psychology
+    affiliation: Yale University
     location: CT, USA, 06511
   - name: Edwina R Orchard
-    department: School of Psychology
-    affiliation: Department of Psychology
+    department: Department of Psychology
+    affiliation: Yale University
     location: CT, USA, 06511
   - name: Avram Holmes
-    department: School of Psychology
-    affiliation: Department of Psychology
+    department: Department of Psychology
+    affiliation: Yale University
     location: CT, USA, 06511
-abstract: Add words here. 
 keywords:
-  - Brain Visualization
-  - MRI Visualization
+  - Neuroimaging visualization
+  - Reproducibility 
+  - Programmatic figures
+  - Open Science
+  - R
 output: 
+  bookdown::word_document2:
+    toc: false
   bookdown::pdf_book:
@@
     keep_tex: true
-    latex_engine: xelatex
-  bookdown::word_document2:
-    toc: false
+    latex_engine: lualatex
 linestretch: 2
@@
 \
+**Table 1. Examples of code-based neuroimaging visualizations tools that can be accessed directly within R, MATLAB and Python environments.**
 
++------------------------+-----------+-----------+-----------+-----------+-------------+
 |                        | Voxel     | Vertex    | ROI       | Edge      | Streamlines |
-|:--------------------------------|:-----:|:------:|:---:|:----:|:-----------:|
-| R                               |       |        |     |      |             |
++:=======================+:==========+:==========+:==========+:==========+:============+
+| **R**                  |           |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+|  ANTsR                 | ✓         | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| brainconn              |           |           |           | ✓         |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| brainR                 | ✓         |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | ciftitools             | ✓         | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | fsbrain                | ✓         | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| ggseg                  |           |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| neurobase              | ✓         |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | oro.nifti              | ✓         |           |           |           |             |
-| neurobase                       |   ✓   |        |     |      |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| **Python**             |           |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| ANTsPy                 | ✓         | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| brainiak               | ✓         |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Brainplotlib           |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Brainspace/surfplot    |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| DIPY                   | ✓         |           |           |           | ✓           |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| ENIGMA toolbox         |           |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| FSLeyes                | ✓         | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | ggseg                  |           |           | ✓         |           |             |
-| brainconn                       |       |        |     |  ✓   |             |
-| Python                          |       |        |     |      |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| graphpype              |           |           |           | ✓         |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| MMVT                   |           | ✓         | ✓         | ✓         |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| MNE                    | ✓         | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| mrivis                 | ✓         |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| NaNSlice               | ✓         |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| netneurotools          |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| nilearn                | ✓         | ✓         | ✓         | ✓         |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| niwidget               | ✓         | ✓         |           |           | ✓           |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Pycortex               | ✓         | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| pySurfer               |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | surfice                | ✓         | ✓         | ✓         | ✓         | ✓           |
-| nilearn                         |   ✓   |   ✓    |  ✓  |  ✓   |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| surfplot               |           | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | Visbrain               | ✓         | ✓         | ✓         | ✓         |             |
-| Pycortex                        |   ✓   |   ✓    | ✓\* |      |             |
-| pySurfer                        |       |   ✓    | ✓\* |      |             |
-| Brainspace/surfplot             |       |   ✓    | ✓\* |      |             |
-| netneurotools                   |       |   ✓    | ✓\* |      |             |
-| Brainplotlib                    |       |   ✓    | ✓\* |      |             |
-| DIPY                            |   ✓   |        |     |      |      ✓      |
-| mrivis                          |   ✓   |        |     |      |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| **MATLAB**             |           |           |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| BrainNetViewer         | ✓         |           | ✓         | ✓         |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Brainspace             |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Brainstorm             | ✓         | ✓         | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| bspmview               | ✓         |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| CandlabCore            | ✓         |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| ECoG/fMRI Vis toolbox  |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | ENIGMA toolbox         |           |           | ✓         |           |             |
-| ggseg                           |       |        |  ✓  |      |             |
-| graphpype                       |       |        |     |  ✓   |             |
-| MATLAB                          |       |        |     |      |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| FieldTrip              | ✓         | ✓         |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| Lead-DBS               | ✓         |           | ✓         |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| mni2fs                 |           | ✓         |           |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| mrtools                | ✓         | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
+| plotSurfaceROIBoundary |           | ✓         | ✓\*       |           |             |
++------------------------+-----------+-----------+-----------+-----------+-------------+
 | Vistasoft              | ✓         | ✓         | ✓         |           | ✓           |
-| BrainNetViewer                  |   ✓   |        |  ✓  |  ✓   |             |
-| mrtools                         |   ✓   |   ✓    | ✓\* |      |             |
-| FieldTrip                       |   ✓   |   ✓    |     |      |             |
-| ECoG/fMRI visualization toolbox |       |   ✓    | ✓\* |      |             |
-| plotSurfaceROIBoundary          |       |   ✓    | ✓\* |      |             |
-| Brainspace                      |       |   ✓    | ✓\* |      |             |
-| CandlabCore                     |   ✓   |        |  ✓  |      |             |
-| ENIGMA toolbox                  |       |        |  ✓  |      |             |
-
++------------------------+-----------+-----------+-----------+-----------+-------------+
+Note: The tools listed contain functionality to generate at least close-to-publication-ready neuroimaging figures via user-entered code within R, MATLAB and Python environments.This list does not include cross-platform general purpose visualization software.
 \
+\*Cortex only
 
@@
 
-patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]|(figs[[3]]/figs[[4]]/figs[[10]])
+patchwork <- figs[[1]]/figs[[2]]|((figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[3]]/figs[[4]]/figs[[10]])+plot_layout(heights = c(0.5,1,1)))
 
@@
 Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes).
-Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
-Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.
+Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
+Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.
+
+As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time.
+While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools.
+Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.
 
@@
 
-### Supplement (Code used to generate figure)
+# Supplement (Code used to generate Figures)
 
@@
 
-#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)
+#Set the breaks/intervals you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)
 breaks = seq(.3,.6, by=0.005)
@@
        NA.x = T,       #Do not display NA values
-       col.y= viridis::viridis(n = 500), #Select the colour scale. In this case I have used the viridis scale from the viridis package. 
+       col.y= viridis::viridis(n = 500), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
        xyz = c(70,50,80), #set the x y & z slice you want to visualise
        useRaster = T,     #Sometimes using Raster makes for clearer plots
-       ycolorbar = TRUE, #Add a colorbar
+       ycolorbar = TRUE,  #Add a color bar
        mfrow = c(1,1)) + 
@@
 library(fsbrain)
+library(rgl)
 
@@
 
-colourmap <- colorRampPalette(viridis::viridis(n = 10000))
+colourmap <- colorRampPalette(viridis::viridis(n = 1000))
 fsbrain.set.default.figsize(700, 700);
 
-cm = vis.subject.morph.standard(subjects_dir, 
+brain = vis.subject.morph.native(subjects_dir, 
                                 subject_id, 'sulc', 
-                                fwhm='10', 
                                 cortex_only = T, 
                                 views=NULL, 
+                                draw_colorbar = FALSE,
                                 makecmap_options = list('colFn'=colourmap))
-img = export(cm, colorbar_legend='Effect', output_img = "data/fig1d.png")
 
-rgl.snapshot("data/fig1d.png")
-rgl.close()
+img = export(brain, draw_colorbar = FALSE, output_img = "data/fig1d.png")
 

### 2022-04-23 manuscript.tex
.

@@
    \\
-    School of Psychology \\
     Department of Psychology \\
+    Yale University \\
   CT, USA, 06511 \\
@@
 \begin{abstract}
-Add words here.
+
 \end{abstract}
@@
 \keywords{
-    Brain Visualization
+    Neuroimaging visualization
    \and
-    MRI Visualization
+    Reproducibility
+   \and
+    Programmatic figures
+   \and
+    Open Science
+   \and
+    R
   }
@@
 \hfill\break
+\textbf{Table 1. Examples of code-based neuroimaging visualizations tools that can be accessed directly within R, MATLAB and Python environments.}
 
-\begin{longtable}[]{@{}lccccc@{}}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.29}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.16}}@{}}
 \toprule
@@
 \endhead
-R & & & & & \\
+\textbf{R} & & & & & \\
+ANTsR & ✓ & ✓ & ✓ & & \\
+brainconn & & & & ✓ & \\
+brainR & ✓ & & ✓ & & \\
 ciftitools & ✓ & ✓ & ✓* & & \\
 fsbrain & ✓ & ✓ & ✓* & & \\
+ggseg & & & ✓ & & \\
+neurobase & ✓ & & & & \\
 oro.nifti & ✓ & & & & \\
-neurobase & ✓ & & & & \\
+\textbf{Python} & & & & & \\
+ANTsPy & ✓ & ✓ & ✓ & & \\
+brainiak & ✓ & & & & \\
+Brainplotlib & & ✓ & ✓* & & \\
+Brainspace/surfplot & & ✓ & ✓* & & \\
+DIPY & ✓ & & & & ✓ \\
+ENIGMA toolbox & & & ✓ & & \\
+FSLeyes & ✓ & ✓ & ✓ & & \\
 ggseg & & & ✓ & & \\
-brainconn & & & & ✓ & \\
-Python & & & & & \\
-surfice & ✓ & ✓ & ✓ & ✓ & ✓ \\
+graphpype & & & & ✓ & \\
+MMVT & & ✓ & ✓ & ✓ & \\
+MNE & ✓ & ✓ & ✓ & & \\
+mrivis & ✓ & & & & \\
+NaNSlice & ✓ & & & & \\
+netneurotools & & ✓ & ✓* & & \\
 nilearn & ✓ & ✓ & ✓ & ✓ & \\
-Visbrain & ✓ & ✓ & ✓ & ✓ & \\
+niwidget & ✓ & ✓ & & & ✓ \\
 Pycortex & ✓ & ✓ & ✓* & & \\
 pySurfer & & ✓ & ✓* & & \\
-Brainspace/surfplot & & ✓ & ✓* & & \\
-netneurotools & & ✓ & ✓* & & \\
-Brainplotlib & & ✓ & ✓* & & \\
-DIPY & ✓ & & & & ✓ \\
-mrivis & ✓ & & & & \\
+surfice & ✓ & ✓ & ✓ & ✓ & ✓ \\
+surfplot & & ✓ & ✓ & & \\
+Visbrain & ✓ & ✓ & ✓ & ✓ & \\
+\textbf{MATLAB} & & & & & \\
+BrainNetViewer & ✓ & & ✓ & ✓ & \\
+Brainspace & & ✓ & ✓* & & \\
+Brainstorm & ✓ & ✓ & ✓ & & \\
+bspmview & ✓ & & ✓ & & \\
+CandlabCore & ✓ & & ✓ & & \\
+ECoG/fMRI Vis toolbox & & ✓ & ✓* & & \\
 ENIGMA toolbox & & & ✓ & & \\
-ggseg & & & ✓ & & \\
-graphpype & & & & ✓ & \\
-MATLAB & & & & & \\
+FieldTrip & ✓ & ✓ & & & \\
+Lead-DBS & ✓ & & ✓ & & \\
+mni2fs & & ✓ & & & \\
+mrtools & ✓ & ✓ & ✓* & & \\
+plotSurfaceROIBoundary & & ✓ & ✓* & & \\
 Vistasoft & ✓ & ✓ & ✓ & & ✓ \\
-BrainNetViewer & ✓ & & ✓ & ✓ & \\
-mrtools & ✓ & ✓ & ✓* & & \\
-FieldTrip & ✓ & ✓ & & & \\
-ECoG/fMRI visualization toolbox & & ✓ & ✓* & & \\
-plotSurfaceROIBoundary & & ✓ & ✓* & & \\
-Brainspace & & ✓ & ✓* & & \\
-CandlabCore & ✓ & & ✓ & & \\
-ENIGMA toolbox & & & ✓ & & \\
 \bottomrule
@@
 
-\hfill\break
+Note: The tools listed contain functionality to generate at least close-to-publication-ready neuroimaging figures via user-entered code within R, MATLAB and Python environments.This list does not include cross-platform general purpose visualization software.\\
+*Cortex only
 
@@
 Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes).
-Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
-Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.
+Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
+Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.
+
+As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time.
+While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools.
+Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.
 
@@
 
-\hypertarget{supplement-code-used-to-generate-figure}{%
-\subsubsection{Supplement (Code used to generate figure)}\label{supplement-code-used-to-generate-figure}}
+\hypertarget{supplement-code-used-to-generate-figures}{%
+\section{Supplement (Code used to generate Figures)}\label{supplement-code-used-to-generate-figures}}
 
@@
 
-\CommentTok{\#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)}
+\CommentTok{\#Set the breaks/intervals you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)}
 \NormalTok{breaks }\OtherTok{=} \FunctionTok{seq}\NormalTok{(.}\DecValTok{3}\NormalTok{,.}\DecValTok{6}\NormalTok{, }\AttributeTok{by=}\FloatTok{0.005}\NormalTok{)}
@@
        \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
-       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the colour scale.
+       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the color scale.
 In this case I have used the viridis scale from the viridis package.
@@
        \AttributeTok{useRaster =}\NormalTok{ T,     }\CommentTok{\#Sometimes using Raster makes for clearer plots}
-       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{, }\CommentTok{\#Add a colorbar}
+       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{,  }\CommentTok{\#Add a color bar}
        \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
@@
 \FunctionTok{library}\NormalTok{(fsbrain)}
+\FunctionTok{library}\NormalTok{(rgl)}
 
@@
 
-\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{10000}\NormalTok{))}
+\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
 \FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}
 
-\NormalTok{cm }\OtherTok{=} \FunctionTok{vis.subject.morph.standard}\NormalTok{(subjects\_dir, }
+\NormalTok{brain }\OtherTok{=} \FunctionTok{vis.subject.morph.native}\NormalTok{(subjects\_dir, }
 \NormalTok{                                subject\_id, }\StringTok{\textquotesingle{}sulc\textquotesingle{}}\NormalTok{, }
-                                \AttributeTok{fwhm=}\StringTok{\textquotesingle{}10\textquotesingle{}}\NormalTok{, }
                                 \AttributeTok{cortex\_only =}\NormalTok{ T, }
                                 \AttributeTok{views=}\ConstantTok{NULL}\NormalTok{, }
+                                \AttributeTok{draw\_colorbar =} \ConstantTok{FALSE}\NormalTok{,}
                                 \AttributeTok{makecmap\_options =} \FunctionTok{list}\NormalTok{(}\StringTok{\textquotesingle{}colFn\textquotesingle{}}\OtherTok{=}\NormalTok{colourmap))}
-\NormalTok{img }\OtherTok{=} \FunctionTok{export}\NormalTok{(cm, }\AttributeTok{colorbar\_legend=}\StringTok{\textquotesingle{}Effect\textquotesingle{}}\NormalTok{, }\AttributeTok{output\_img =} \StringTok{"data/fig1d.png"}\NormalTok{)}
 
-\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1d.png"}\NormalTok{)}
-\FunctionTok{rgl.close}\NormalTok{()}
+\NormalTok{img }\OtherTok{=} \FunctionTok{export}\NormalTok{(brain, }\AttributeTok{draw\_colorbar =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{output\_img =} \StringTok{"data/fig1d.png"}\NormalTok{)}
 \end{Highlighting}

### 2022-04-25 manuscript.Rmd
fig fix

@@
 output: 
-  bookdown::word_document2:
-    toc: false
   bookdown::pdf_book:
@@
     latex_engine: lualatex
+  bookdown::word_document2:
+    toc: false
 linestretch: 2
@@
 Most code-based tools also come with documentation, with R-packages on the *CRAN* or *Neuroconductor* (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance.
-Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, & Mejia, 2022; Mowinckel & Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer & Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users.
+Recent packages have started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, & Mejia, 2022; Mowinckel & Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer & Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users.
 As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.
@@
 Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.
-*e-Life*, *Aperture Neuro*), with other journals like *F1000Research* and *GigaScience* even allowing on-demand re-running of code computational environment linked to the associated article using 'compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),
+*e-Life*, *Aperture Neuro*), with other journals like *F1000Research* and *GigaScience* even allowing on-demand re-running of code computational environment linked to the associated article using 'compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021).
 
@@
 Often cerebellar and brain-stem regions are not well represented in software (e.g.
-Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes).
+Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes, 2022).
 Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
@@
 While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools.
-Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.
+Future work should continue to consolidate brain visualization methods into unified beginner-friendly code-based tools which are capable of plotting multiple data types.
 
@@
 
-patchwork <- figs[[1]]/figs[[2]]|(figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]|(figs[[3]]/figs[[4]]/figs[[10]])
-
+patchwork <- figs[[1]]/figs[[2]]|((figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[3]]/figs[[4]]/figs[[10]])+plot_layout(heights = c(0.7,1,1)))
 patchwork + plot_annotation(tag_levels = 'A',
@@
 library(neurobase)
-library(ggplotify)
 
@@
        NA.x = T,       #Do not display NA values
-       col.y= viridis::viridis(n = 500), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
+       col.y= rev(viridis::inferno(n = 500)), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
        xyz = c(70,50,80), #set the x y & z slice you want to visualise
@@
        mfrow = c(1,1)) + 
-  colorbar(breaks,col = viridis::viridis(n=length(breaks)-1), 
+  colorbar(breaks, col = rev(viridis::inferno(n=length(breaks)-1)), 
            text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar
@@
         z=c(seq(30,110,10)), 
-        col.y =  alpha(rainbow(300), 0.3),
+        col.y =  alpha(viridis::inferno(300), 0.6),
         plane = "axial",  
@@
                    idx = 1,
-                   colors = viridis::viridis(n = 100),
+                   colors = viridis::plasma(n = 100),
                    zlim = c(1.2,1.5),  
@@
 
-colourmap <- colorRampPalette(viridis::viridis(n = 1000))
+colourmap <- colorRampPalette(viridis::plasma(n = 1000))
 fsbrain.set.default.figsize(700, 700);
@@
 
-#remotes::install_github("sidchop/brainconn")
+#devtools::install_github("sidchop/brainconn")
 library(brainconn)
@@
 degree <- rowSums(conmat)[which(rowSums(conmat)!=0)]
-fig1h <- brainconn(atlas ="schaefer300_n7", 
+
+brainconn(atlas ="schaefer300_n7", 
                    conmat=conmat, 
                    node.size = degree/2,
-                   view="ortho", 
+                   view="top", 
                    edge.color.weighted = T,
-                   background.alpha = 0.4, 
+                   background.alpha = 0.8, 
                    show.legend = F, 
-                   edge.color = scale_edge_colour_gradient2(low='yellow', mid='orange', high='red')) 
+                   edge.color = scale_edge_colour_viridis())
+
 ggsave(filename = 'data/fig1h.png', 

### 2022-04-25 manuscript.tex
fig fix

@@
 Most code-based tools also come with documentation, with R-packages on the \emph{CRAN} or \emph{Neuroconductor} (Muschelli et al., 2019) repositories having compulsory requirements for detailed guidance.
-Recent packages have even started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, \& Mejia, 2022; Mowinckel \& Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer \& Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users.
+Recent packages have started to include detailed documentation in GitHub repositories, or even entire papers (e.g., Pham, Muschelli, \& Mejia, 2022; Mowinckel \& Vidal-Piñeiro, 2020; Huntenburg et at., 2017; Schäfer \& Ecker, 2020) which provide examples of figures which can be used as starting points or templates for new users.
 As the popularity of code-sharing for figure increases, there will be a cornucopia of templates that can be used as the basis for new figures.
@@
 For instance, a fully reproducible version of the current paper can be found on \href{https://github.com/sidchop/Brain_comms_field_potential}{GitHub}.
-Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.~\emph{e-Life}, \emph{Aperture Neuro}), with other journals like \emph{F1000Research} and \emph{GigaScience} even allowing on-demand re-running of code computational environment linked to the associated article using `compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021),
+Some journals that publish neuroimaging studies are moving towards allowing reproducible manuscripts, including reproducible figures (e.g.~\emph{e-Life}, \emph{Aperture Neuro}), with other journals like \emph{F1000Research} and \emph{GigaScience} even allowing on-demand re-running of code computational environment linked to the associated article using `compute capsules' from the cloud-based platform Code Ocean (Code Ocean, 2021).
 
@@
 
-Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes).
+Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes, 2022).
 Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize.
@@
 \FunctionTok{library}\NormalTok{(neurobase)}
-\FunctionTok{library}\NormalTok{(ggplotify)}
 
@@
        \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
-       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the color scale.
+       \AttributeTok{col.y=} \FunctionTok{rev}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{)), }\CommentTok{\#Select the color scale.
 In this case I have used the viridis scale from the viridis package.
@@
        \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
-  \FunctionTok{colorbar}\NormalTok{(breaks,}\AttributeTok{col =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{), }
+  \FunctionTok{colorbar}\NormalTok{(breaks, }\AttributeTok{col =} \FunctionTok{rev}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{)), }
            \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}
@@
         \AttributeTok{z=}\FunctionTok{c}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{30}\NormalTok{,}\DecValTok{110}\NormalTok{,}\DecValTok{10}\NormalTok{)), }
-        \AttributeTok{col.y =}  \FunctionTok{alpha}\NormalTok{(}\FunctionTok{rainbow}\NormalTok{(}\DecValTok{300}\NormalTok{), }\FloatTok{0.3}\NormalTok{),}
+        \AttributeTok{col.y =}  \FunctionTok{alpha}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{inferno}\NormalTok{(}\DecValTok{300}\NormalTok{), }\FloatTok{0.6}\NormalTok{),}
         \AttributeTok{plane =} \StringTok{"axial"}\NormalTok{,  }
@@
                    \AttributeTok{idx =} \DecValTok{1}\NormalTok{,}
-                   \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{),}
+                   \AttributeTok{colors =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{plasma}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{),}
                    \AttributeTok{zlim =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.2}\NormalTok{,}\FloatTok{1.5}\NormalTok{),  }
@@
 
-\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
+\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{plasma}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
 \FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}
@@
 
-\CommentTok{\#remotes::install\_github("sidchop/brainconn")}
+\CommentTok{\#devtools::install\_github("sidchop/brainconn")}
 \FunctionTok{library}\NormalTok{(brainconn)}
@@
 \NormalTok{degree }\OtherTok{\textless{}{-}} \FunctionTok{rowSums}\NormalTok{(conmat)[}\FunctionTok{which}\NormalTok{(}\FunctionTok{rowSums}\NormalTok{(conmat)}\SpecialCharTok{!=}\DecValTok{0}\NormalTok{)]}
-\NormalTok{fig1h }\OtherTok{\textless{}{-}} \FunctionTok{brainconn}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
+
+\FunctionTok{brainconn}\NormalTok{(}\AttributeTok{atlas =}\StringTok{"schaefer300\_n7"}\NormalTok{, }
                    \AttributeTok{conmat=}\NormalTok{conmat, }
                    \AttributeTok{node.size =}\NormalTok{ degree}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
-                   \AttributeTok{view=}\StringTok{"ortho"}\NormalTok{, }
+                   \AttributeTok{view=}\StringTok{"top"}\NormalTok{, }
                    \AttributeTok{edge.color.weighted =}\NormalTok{ T,}
-                   \AttributeTok{background.alpha =} \FloatTok{0.4}\NormalTok{, }
-                   \AttributeTok{show.legend =}\NormalTok{ F,}
-                   \AttributeTok{edge.color =} \FunctionTok{scale\_edge\_colour\_gradient2}\NormalTok{(}\AttributeTok{low=}\StringTok{\textquotesingle{}yellow\textquotesingle{}}\NormalTok{, }\AttributeTok{mid=}\StringTok{\textquotesingle{}orange\textquotesingle{}}\NormalTok{, }\AttributeTok{high=}\StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{)) }
+                   \AttributeTok{background.alpha =} \FloatTok{0.8}\NormalTok{, }
+                   \AttributeTok{show.legend =}\NormalTok{ F, }
+                   \AttributeTok{edge.color =} \FunctionTok{scale\_edge\_colour\_viridis}\NormalTok{()) }
+
 \FunctionTok{ggsave}\NormalTok{(}\AttributeTok{filename =} \StringTok{\textquotesingle{}data/fig1h.png\textquotesingle{}}\NormalTok{, }
